---
title: "RP2 - Final"
author: "Mubashir Sultan"
date: "6/10/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries and initial setup,  include=FALSE}
# sometimes tidy doesn't load
# remove.packages("rlang")
# install.packages("rlang")

# loading libraries
library(here)
library(readxl)
library(tidyverse)
library(jtools)
# library(LaCroixColoR)
library(ggpubr)
# library(scales)

# model
# library(lme4)
library(GGally)
library(brms)
# library(sjPlot)
library(emmeans)
library(multcomp)
library(rstatix)
library(texreg)
```

```{r colour}

# The palette with grey:
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```

```{r loading in cleaned dataset}
# dat
dat <- read_excel(here::here("Data", "Clean", "cleaned_data.xlsx"))


# add dat from pretest
# item numbers¸
item_number_index <- unique(dat$item_number)

pretest_batch_1 <- read_excel(here::here("Data", "Misc", "final_items_after_pretest_batch_1.xlsx"), sheet = 1, col_names = TRUE, col_types = NULL)

pretest_batch_2 <- read_excel(here::here("Data", "Misc", "final_items_after_pretest_batch_2.xlsx"), sheet = 1, col_names = TRUE, col_types = NULL)

pretest <- rbind(pretest_batch_1, pretest_batch_2)

# cleaning up workspace
rm(list = c("pretest_batch_1", "pretest_batch_2"))


```

adding whether the item is true or false, which politicial party does the item favour, and participant accuracy
```{r adding true and false and item dem/rep column df}
# setting up a col
dat$item_accuracy <- NA
dat$item_political_leaning <- NA

# string detect all of the values that are item number x and then add that to item_accuracy of my df
for (i in 1:length(item_number_index)) {
  # get index of all of those that have item_number i as item number
  index_my_df <- str_detect(dat$item_number, paste0("\\b", item_number_index[i], "\\b"))
  # get value of whether item number i is true or false
  true_false_value_from_df_pretest <- pretest$Category[pretest$item_number == item_number_index[i]]
  item_dem_rep_value_from_df_pretest <- pretest$pretest_combined_categ[pretest$item_number == item_number_index[i]]
  # subset using index and value
  dat$item_accuracy[index_my_df] <- true_false_value_from_df_pretest
  dat$item_political_leaning[index_my_df] <- item_dem_rep_value_from_df_pretest
}

# adjusting values to True News and False News
dat$item_accuracy[str_detect(dat$item_accuracy, "True")] <- "True News"
dat$item_accuracy[str_detect(dat$item_accuracy, "False")] <- "False News"

# making into factor 
dat$item_accuracy <- factor(dat$item_accuracy, levels = c("False News", "True News"))


# adding baseline accuracy column
dat <- dat %>% mutate(part_accuracy = ifelse(item_accuracy == "False News" & accuracy_response == "No", TRUE,
  ifelse(item_accuracy == "True News" & accuracy_response == "Yes", TRUE, FALSE)
))
```


preparing classes and so on
```{r preparing dat class for analysis,  include=FALSE}
# changing Time Pressure to Time Pressure and such
dat <- dat %>% mutate(condition = 
                          case_when(condition == "time_pressure" ~ "Time Pressure",
                                    condition == "non_time_pressure" ~ "Control"))

# making into factor 
dat$condition <- factor(dat$condition, levels = c("Control", "Time Pressure"))

# into numeric
dat$condition_num <- as.factor(as.numeric(dat$condition) - 1)

dat$ID <- as.factor(dat$ID)
dat$Subject <- as.factor(dat$Subject)
dat$item_number <- as.factor(as.numeric(dat$item_number))
dat$trial_number <- as.factor(as.numeric(dat$trial_number))

dat$accuracy_response <- factor(dat$accuracy_response, levels = c("No", "Yes"))
dat$accuracy_timer <- as.numeric(dat$accuracy_timer)

dat$confidence_response <- as.factor(dat$confidence_response)
dat$confidence_timer <- as.numeric(dat$confidence_timer)

# removing "undefined" first
dat$familiarity_response[dat$familiarity_response == "undefined"] <- NA
dat$familiarity_response <- factor(dat$familiarity_response, levels = c("No", "Yes"))
dat$familiarity_timer <- as.numeric(dat$familiarity_timer)

# converting miliseconds into minutes
dat$timerFirstBlock <- as.numeric(dat$timerFirstBlock)
dat$timerFirstBlock <- dat$timerFirstBlock / 60000

dat$timerSecondBlock <- as.numeric(dat$timerSecondBlock)
dat$timerSecondBlock <- dat$timerSecondBlock / 60000

dat$overallTime <- as.numeric(dat$overallTime)
dat$overallTime <- dat$overallTime / 60000

# adding class to numeric
dat$bonus <- as.numeric(dat$bonus)

# converting miliseconds into seconds
dat$accuracy_timer <- dat$accuracy_timer / 1000
dat$confidence_timer <- dat$confidence_timer / 1000
dat$familiarity_timer <- dat$familiarity_timer / 1000

# adding political leaning column
# values for scale
# 1 = Strongly Democratic
# 2 = Moderately Democratic
# 3 = Lean Democratic
# 4 = Strongly Republican
# 5 = Moderately Republican
# 6 = Lean Republican
dat$political_identification_scale <- as.numeric(dat$political_identification_scale)
dat <- dat %>% mutate(political_identity = ifelse(political_identification_scale <= 3, "Democrat", "Republican"))

# recoding to include scale labels
dat <- dat %>% mutate(political_identification_scale = 
        case_when(political_identification_scale == 1 ~ "Strongly Democratic",
                  political_identification_scale == 2 ~ "Moderately Democratic",
                  political_identification_scale == 3 ~ "Lean Democratic",
                  political_identification_scale == 4 ~ "Lean Republican",
                  political_identification_scale == 5 ~ "Moderately Republican",
                  political_identification_scale == 6 ~ "Strongly Republican"
                  )
        )


# adding class to gender and political leaning
dat$political_identity <- factor(dat$political_identity, levels = c("Republican", "Democrat"))
dat$political_identification_scale <- factor(dat$political_identification_scale, levels = c("Strongly Republican", 
                                                                                            "Moderately Republican", 
                                                                                            "Lean Republican",
                                                                                            "Lean Democratic",
                                                                                            "Moderately Democratic",
                                                                                            "Strongly Democratic"
                                                                                            ))
dat$gender <- as.factor(dat$gender)


# adding class to political interest
dat$political_interest_1 <- factor(dat$political_interest_1, levels = c("Not at all interested", "Slightly interested", "Moderately interested", "Very interested", "Extremely interested"))
dat$political_interest_2 <- factor(dat$political_interest_2)

# adding class to news consumption
dat$news_consumption_1 <- as.factor(dat$news_consumption_1)
dat$news_consumption_2 <- as.factor(dat$news_consumption_2)

# adding congruency
dat <- dat %>% mutate(congruency = 
        case_when(political_identity == "Democrat" & item_political_leaning == "Dem Favoured" ~ "Congruent",
                  political_identity == "Democrat" & item_political_leaning == "Rep Favoured" ~ "Incongruent",
                  political_identity == "Republican" & item_political_leaning == "Rep Favoured" ~ "Congruent",
                  political_identity == "Republican" & item_political_leaning == "Dem Favoured" ~ "Incongruent"))



dat <- dat %>% mutate(congruency_non_binary = 
                  # for congruent 
        case_when(political_identification_scale == "Strongly Democratic" & item_political_leaning == "Dem Favoured" ~ "Strongly Congruent",
                  political_identification_scale == "Moderately Democratic" & item_political_leaning == "Dem Favoured" ~ "Moderately Congruent",
                  political_identification_scale == "Lean Democratic" & item_political_leaning == "Dem Favoured" ~ "Lean Congruent",
                  political_identification_scale == "Lean Republican" & item_political_leaning == "Rep Favoured" ~ "Lean Congruent",
                  political_identification_scale == "Moderately Republican" & item_political_leaning == "Rep Favoured" ~ "Moderately Congruent",
                  political_identification_scale == "Strongly Republican" & item_political_leaning == "Rep Favoured" ~ "Strongly Congruent",
                  
                  # for incongruent
                  political_identification_scale == "Strongly Democratic" & item_political_leaning == "Rep Favoured" ~ "Strongly Incongruent",
                  political_identification_scale == "Moderately Democratic" & item_political_leaning == "Rep Favoured" ~ "Moderately Incongruent",
                  political_identification_scale == "Lean Democratic" & item_political_leaning == "Rep Favoured" ~ "Lean Incongruent",
                  political_identification_scale == "Lean Republican" & item_political_leaning == "Dem Favoured" ~ "Lean Incongruent",
                  political_identification_scale == "Moderately Republican" & item_political_leaning == "Dem Favoured" ~ "Moderately Incongruent",
                  political_identification_scale == "Strongly Republican" & item_political_leaning == "Dem Favoured" ~ "Strongly Incongruent"
                  ))

# making factor
dat$congruency <- factor(dat$congruency, levels = c("Incongruent", "Congruent"))

dat$congruency_non_binary <- factor(dat$congruency_non_binary, levels = c("Strongly Incongruent", "Moderately Incongruent", "Lean Incongruent", "Lean Congruent", "Moderately Congruent", "Strongly Congruent"))



# truce false for familiarity
dat <- dat %>% mutate(binary_familiarity = ifelse(familiarity_response == "Yes", TRUE, FALSE))
dat <- dat %>% mutate(binary_accuracy = ifelse(accuracy_response == "Yes", TRUE, FALSE))

# adding class to batch
dat$batch <- as.factor(dat$batch)

# item numbers
item_number_index <- unique(dat$item_number)


# addng class for age
dat$age <- as.numeric(dat$age)


# confidence scale renamed
dat <- dat %>%
  mutate(confidence_percent = case_when(
    confidence_response == 1 ~ 50,
    confidence_response == 2 ~ 60,
    confidence_response == 3 ~ 70,
    confidence_response == 4 ~ 80,
    confidence_response == 5 ~ 90,
    confidence_response == 6 ~ 100
  ))

# CRT levels
dat$CRT_binary <- factor(dat$CRT_binary, levels = c("Low", "High"))
dat$CRT_binary <- recode_factor(dat$CRT_binary, Low = "CRT Low", High = "CRT High")

# levels of accuracy per second
dat <- dat %>% mutate(
  second_bins =
    ifelse(accuracy_timer <= 1, "One",
      ifelse(accuracy_timer > 1 & accuracy_timer <= 2, "Two",
        ifelse(accuracy_timer > 2 & accuracy_timer <= 3, "Three",
          ifelse(accuracy_timer > 3 & accuracy_timer <= 4, "Four",
            ifelse(accuracy_timer > 4 & accuracy_timer <= 5, "Five",
              ifelse(accuracy_timer > 5 & accuracy_timer <= 6, "Six",
                ifelse(accuracy_timer > 6 & accuracy_timer <= 7, "Seven",
                  ifelse(accuracy_timer > 7 & accuracy_timer <= 8, "Eight",
                    ifelse(accuracy_timer > 8 & accuracy_timer <= 9, "Nine",
                      ifelse(accuracy_timer > 9 & accuracy_timer <= 10, "Ten",
                        ifelse(accuracy_timer > 10 & accuracy_timer <= 11, "Eleven",
                          ifelse(accuracy_timer > 11 & accuracy_timer <= 12, "Twelve",
                            ifelse(accuracy_timer > 12 & accuracy_timer <= 13, "Thirteen",
                              ifelse(accuracy_timer > 13 & accuracy_timer <= 14, "Fourteen",
                                ifelse(accuracy_timer > 14 & accuracy_timer <= 15, "Fifteen",
                                  ifelse(accuracy_timer > 15 & accuracy_timer <= 16, "Sixteen",
                                    ifelse(accuracy_timer > 16 & accuracy_timer <= 17, "Seventeen",
                                      ifelse(accuracy_timer > 17 & accuracy_timer <= 18, "Eighteen",
                                        ifelse(accuracy_timer > 18 & accuracy_timer <= 19, "Nineteen",
                                          ifelse(accuracy_timer > 19 & accuracy_timer <= 20, "Twenty",
                                            "Twenty +"
                                          )
                                        )
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    )
)


# adding factor
dat$second_bins <- factor(dat$second_bins, levels = c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten", "Eleven", "Twelve", "Thirteen", "Fourteen", "Fifteen", "Sixteen", "Seventeen", "Eighteen", "Nineteen", "Twenty", "Twenty +"))
```


removing data points that exceed 6 seconds for time pressure treatment and 60 seconds for control treatment
```{r}

# capping accuracy timer removing those trial that go beyond 6 seconds in time pressure
dat <- dat %>% 
  mutate(accuracy_timer_cap = F,
         accuracy_timer_cap = ifelse(condition == "Control" & accuracy_timer > 60, T,
                                     ifelse(condition == "Time Pressure" & accuracy_timer > 6, T, accuracy_timer_cap)))

# checking count
dat %>% group_by(condition) %>% count(accuracy_timer_cap)

# removing from dat
dat <- dat %>%
  filter(accuracy_timer_cap != T)


```


centering vars for model 
```{r scaling vars for model}
# creating binary versions
dat <- dat %>%
  mutate(C_condition = case_when(condition == "Control" ~ 0, condition == "Time Pressure" ~ 1),
         C_item_accuracy = case_when(item_accuracy == "False News" ~ 0, item_accuracy == "True News" ~ 1),
         C_congruency = case_when(congruency == "Incongruent" ~ 0, congruency == "Congruent" ~ 1),
         C_familiarity_response = case_when(familiarity_response == "No" ~ 0, familiarity_response == "Yes" ~ 1),
         C_congruency_non_binary = as.numeric(congruency_non_binary)) #can also be done via case_when and vice versa for others

# now mean centering
dat <- dat %>%
  mutate(C_condition = C_condition - mean(C_condition),
         C_item_accuracy = C_item_accuracy - mean(C_item_accuracy),
         C_congruency = C_congruency - mean(C_congruency),
         C_familiarity_response = C_familiarity_response - mean(C_familiarity_response, na.rm = T),
         )

# to see how CRT is standardised, see 'Making Data' script.

# cogruency standardising
standard_congruency_non_binary <- dat %>%
  summarise(mean = mean(C_congruency_non_binary), SD = sd(C_congruency_non_binary), two_SD = SD*2, count = n(), se = (SD / (sqrt(count))), median = median(C_congruency_non_binary), min = min(C_congruency_non_binary), max = max(C_congruency_non_binary))

# adding standardised values
dat <- dat %>% dplyr::mutate(C_congruency_non_binary = (C_congruency_non_binary - standard_congruency_non_binary$mean[1])/standard_congruency_non_binary$two_SD[1])

```


```{r making a simplified dataset for demogrpahics and such}

dat_demographic <- dat %>% group_by(Subject, condition, PROLIFIC_PID, ID, age, gender, political_identity, political_identification_scale, political_interest_1, political_interest_2, news_consumption_1, news_consumption_2, CRT_1_Clean, CRT_2_Clean, CRT_3_Clean, CRT_4_Clean, CRT_5, CRT_percent, CRT_standard, CRT_binary, overallTime, collection) %>% count()

# adding which batch each participant answered on
dat_demographic$batch <- dat$batch[dat_demographic$Subject]

dat_demographic <- as.data.frame(dat_demographic)


```

list of participants across the various demographic categories
```{r checking all categories}
# making a table for all categories
participants_per_category <- dat_demographic %>% group_by(batch, condition, gender,political_identity) %>% summarise(count = n())
```


# age summary
```{r summary age}

pp_age <- dat_demographic %>%
  # drop_na(age) %>%
  summarise(mean = mean(age), SD = sd(age), count = n(), se = (SD / (sqrt(count))), median = median(age), min = min(age), max = max(age))
```


```{r count per condition}

dat_demographic %>% group_by(condition) %>% count()

```


# time taken plot
```{r general descriptives time taken plot} 

# overall times (in summary)
dat_demographic %>%
  drop_na(overallTime) %>%
  ggplot(aes(x = Subject, y = overallTime, fill = condition)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Overall Time Taken", x = "Participant Number", y = "Minutes") +
  theme(text = element_text(size = 7), axis.text.x = element_text(angle = 45, hjust = 1))

# overall time
df_time_taken_split <- dat_demographic %>%
  drop_na(overallTime) %>%
  group_by(Subject, condition) %>%
  summarise(mean = mean(overallTime))

df_time_taken <- dat_demographic %>%
  drop_na(overallTime) %>%
  group_by(Subject) %>%
  summarise(mean = mean(overallTime))


colnames(df_time_taken)[2] <- "overallTime"
colnames(df_time_taken_split)[3] <- "overallTime"


df_time_taken_split <- df_time_taken_split %>%
  group_by(condition) %>%
  summarise(mean = mean(overallTime), SD = sd(overallTime), count = n(), se = (SD / (sqrt(count))), median = median(overallTime), min = min(overallTime), max = max(overallTime))

df_time_taken <- df_time_taken %>%
  dplyr::select(Subject, overallTime) %>%
  summarise(mean = mean(overallTime), SD = sd(overallTime), count = n(), se = (SD / (sqrt(count))), median = median(overallTime), min = min(overallTime), max = max(overallTime))


df_time_taken_split %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  theme_apa() +
  labs(title = "Time Taken", x = "Overall Time", y = "Mean Minutes")

df_time_taken %>%
  ggplot(aes(x = "", y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  theme_apa() +
  labs(title = "Time Taken", x = "Overall Time", y = "Mean Minutes")


df_time_taken_split %>%
  ggplot(aes(x = condition, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Time Taken", x = "Overall Time", y = "Median Minutes")

df_time_taken %>%
  ggplot(aes(x = "", y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Time Taken", x = "Overall Time", y = "Median Minutes")
```


# Political demographics
```{r demographics age gender}
# plot the distribution of political leaning and gender
dat_demographic %>%
  drop_na(gender, political_identity) %>%
  dplyr::filter(!gender == "Other") %>%
  ggplot(aes(x = gender, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - Gender x Political Lean", x = "Gender", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  facet_wrap(~batch)

# political strength
dat_demographic %>%
  drop_na(gender, political_identity) %>%
  ggplot(aes(x = political_identification_scale, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - Political Strength", x = "Likert Values", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))

# political interest 1 (How interested are you in information about what's going on in government and politics?)
dat_demographic %>%
  drop_na(gender, political_identity) %>%
  ggplot(aes(x = political_interest_1, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - Political Interest 1", x = "Likert Values", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))

# political interest 2 (During a typical week, how many days do you talk about politics with family or friends?)
dat_demographic %>%
  drop_na(gender, political_identity) %>%
  ggplot(aes(x = political_interest_2, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - Political Interest 2", x = "Likert Values", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5)

# news consumption 1 - main source
dat_demographic %>%
  drop_na(gender, political_identity, news_consumption_1) %>%
  ggplot(aes(x = news_consumption_1, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - News Consumption 1 (main source)", x = "Values", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))

# news consumption 1 - secondary source source
dat_demographic %>%
  drop_na(gender, political_identity, news_consumption_1) %>%
  ggplot(aes(x = news_consumption_2, fill = political_identity)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  labs(title = "Demographics - News Consumption 1 (secondary source)", x = "Values", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))
```

# CRT 
```{r CRT figures}

dat_demographic %>%
  ggplot(aes(x = CRT_binary)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "CRT Correct", x = "CRT", y = "Count", fill = "Political Identity") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5)


# making a CRT long df
CRT_long <- dat_demographic %>% select(Subject, ID, condition, CRT_1_Clean, CRT_2_Clean, CRT_3_Clean, CRT_4_Clean, CRT_percent, CRT_standard, CRT_binary)
CRT_long <- pivot_longer(CRT_long, !c(Subject, ID, condition, CRT_percent, CRT_standard, CRT_binary), names_to = "measurement", values_to = "value")

# removing clean
CRT_long$measurement <- str_replace(CRT_long$measurement, "_Clean", "")

CRT_long %>%
  drop_na(value) %>%
  ggplot(aes(x = as.factor(as.character(value)), fill = condition)) +
  geom_bar(position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "CRT", x = "CRT", y = "Count", fill = "Condition") +
  geom_text(aes(label = ..count..), stat = "count", position = position_dodge2(width = 1), vjust = -.5) +
  facet_grid(~measurement)


CRT_non_scaled <- dat_demographic %>%
  # dplyr::filter(accuracy_timer < 60) %>%
  ggplot(aes(x = CRT_percent)) +
  geom_histogram(bins = 5) +
  # geom_vline(xintercept = CRT_Clean_summary_standard$mean[1], linetype="dotted", color = "grey") +
  scale_x_continuous(breaks = seq(0, 1, .25)) +
  theme_apa() +
  labs(x = "Proportion Correct", y = "Count")

CRT_non_scaled
ggsave(file = here::here("Figures", "CRT_non_scaled.pdf"), plot = CRT_non_scaled)

CRT_scaled <- dat_demographic %>%
  # dplyr::filter(accuracy_timer < 60) %>%
  ggplot(aes(x = CRT_standard)) +
  geom_histogram(bins = 5) +
    # geom_vline(xintercept = CRT_Clean_summary_non_standard$mean[1], linetype="dotted", color = "grey") +
  scale_x_continuous(breaks = c(-1.08, -0.64, -0.19, 0.25, 0.70)) +
  theme_apa() +
  labs(x = "Proportion Correct Standardised", y = "Count")

CRT_scaled
ggsave(file = here::here("Figures", "CRT_scaled.pdf"), plot = CRT_scaled)


CRT_combined <- 
  cowplot::plot_grid(
  CRT_non_scaled,
  CRT_scaled,
  # align = 'vh',
  labels = c("A", "B"),
  # hjust = -1,
  nrow = 1
)

CRT_combined

ggsave(file = here::here("Figures", "CRT_combined.pdf"), width = 7 , height = 4, plot = CRT_combined)


```

# Ideological congruency
```{r ideological congruency figures}

dat %>%
  drop_na(political_identification_scale) %>%
  ggplot(aes(x = political_identification_scale, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Political Identity Scale Histogram", x = "Likert Values", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))

dat %>%
  drop_na(congruency) %>%
  ggplot(aes(x = congruency, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Congruency Histogram", x = "Likert Values", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223"))

 ideological_congruency <- dat %>%
  drop_na(congruency_non_binary) %>%
  ggplot(aes(x = congruency_non_binary)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(x = "Ideological Congruency", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  theme(axis.text.x = element_text(angle = 15, vjust = .5, hjust = .5)) +
  theme(plot.margin = unit(c(0,1.5,0,0), "lines"))

 ideological_congruency
 
 ggsave(file = here::here("Figures", "congruency.pdf"), width = 7 , height = 7, plot = ideological_congruency)

  
ideological_congruency_scaled <- dat %>%
  drop_na(C_congruency_non_binary) %>%
  ggplot(aes(x = C_congruency_non_binary)) +
  geom_histogram(bins = 6) +
  theme_apa() +
  labs(x = "Ideological Congruency Standardised", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223"))

ideological_congruency_scaled



ideological_congruency_combined <- 
  cowplot::plot_grid(
  ideological_congruency,
  ideological_congruency_scaled,
  # align = 'vh',
  labels = c("A", "B"),
  # hjust = -1,
  nrow = 1
)

ideological_congruency_combined

# ggsave(file = here::here("Figures", "congruency_combined.pdf"), width = 7 , height = 4, plot = ideological_congruency_combined)


```

# RT histograms 
```{r times histograms accuracy }
# (in summary)
# Basic histogram Accuracy timer
dat %>%
  dplyr::filter(accuracy_timer < 60) %>%
  ggplot(aes(x = accuracy_timer)) +
  geom_histogram() +
  theme_apa() +
  labs(title = "Accuracy RT Histogram", x = "Seconds", y = "Count") +
  facet_wrap(~condition, scales = "free")

```


```{r times histograms confidence }
# Basic histogram confidence timer
# dat %>% dplyr::filter(confidence_timer < 20) %>% ggplot(aes(x=confidence_timer)) + geom_histogram() + theme_apa() + labs(title = "Confidence RT Histogram", x = "Seconds", y = "Count")

dat %>%
  dplyr::filter(confidence_timer < 15) %>%
  ggplot(aes(x = confidence_timer)) +
  geom_histogram() +
  theme_apa() +
  labs(title = "Confidence RT Histogram", x = "Seconds", y = "Count") +
  facet_wrap(~condition, scales = "free")

```


```{r times histograms familiarity }
# Basic histogram familiarity timer
dat %>%
  dplyr::filter(familiarity_timer < 15) %>%
  ggplot(aes(x = familiarity_timer)) +
  geom_histogram() +
  theme_apa() +
  labs(title = "familiarity RT Histogram", x = "Seconds", y = "Count") +
  facet_wrap(~condition)

```

# Scale histograms
```{r scales histograms accuracy}
# Basic histogram Accuracy scale
dat %>%
  drop_na(accuracy_response) %>%
  dplyr::filter(!accuracy_response == "undefined") %>%
  ggplot(aes(x = accuracy_response, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram", x = "Likert Values", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  facet_wrap(~condition)


#  non-tp
dat %>%
  dplyr::filter(item_number %in% item_number_index[1:15]) %>%
  drop_na(accuracy_response) %>%
  dplyr::filter(!accuracy_response == "undefined") %>%
  ggplot(aes(x = accuracy_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[16:30]) %>%
  drop_na(accuracy_response) %>%
  dplyr::filter(!accuracy_response == "undefined") %>%
  ggplot(aes(x = accuracy_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

#  with-tp
dat %>%
  dplyr::filter(item_number %in% item_number_index[31:45]) %>%
  drop_na(accuracy_response) %>%
  ggplot(aes(x = accuracy_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[46:60]) %>%
  drop_na(accuracy_response) %>%
  dplyr::filter(!accuracy_response == "undefined") %>%
  ggplot(aes(x = accuracy_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[61:75]) %>%
  drop_na(accuracy_response) %>%
  dplyr::filter(!accuracy_response == "undefined") %>%
  ggplot(aes(x = accuracy_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Accuracy Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)
```


```{r scales histograms confidence}
# Basic histogram Confidence scale
dat %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram", x = "Likert Values", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  facet_wrap(~condition)

dat %>%
  dplyr::filter(item_number %in% item_number_index[1:15]) %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[16:30]) %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[31:45]) %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[46:60]) %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[61:75]) %>%
  drop_na(confidence_response) %>%
  ggplot(aes(x = confidence_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Confidence Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)
```


```{r scales histograms familiarity}
# Basic histogram familiarity scale
dat %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram", x = "Likert Values", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  facet_wrap(~condition)

# (summary)
dat %>%
  dplyr::filter(item_number %in% item_number_index[1:15]) %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[16:30]) %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram Non-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[31:45]) %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[46:60]) %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)

dat %>%
  dplyr::filter(item_number %in% item_number_index[61:75]) %>%
  drop_na(familiarity_response) %>%
  ggplot(aes(x = familiarity_response)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "familiarity Scale Histogram With-TP (Item Level)", x = "Likert Values", y = "Count") +
  facet_wrap(~item_number)
```

# Response times per item 
```{r timers per item accuracy}
# all items accuracy timer
item_times_accuracy <- dat %>%
  group_by(item_number, condition) %>%
  summarise(mean = mean(accuracy_timer, na.rm = TRUE), SD = sd(accuracy_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_timer, na.rm = TRUE), min = min(accuracy_timer, na.rm = TRUE), max = max(accuracy_timer, na.rm = TRUE))

# item_times_accuracy

# (summary)
item_times_accuracy %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Item", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_accuracy %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

item_times_accuracy %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_accuracy %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Item", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_accuracy %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_accuracy %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)
```


```{r timers per item confidence}
# all items confidence timer
item_times_confidence <- dat %>%
  group_by(item_number, condition) %>%
  summarise(mean = mean(confidence_timer, na.rm = TRUE), SD = sd(confidence_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(confidence_timer, na.rm = TRUE), min = min(confidence_timer, na.rm = TRUE), max = max(confidence_timer, na.rm = TRUE))

# item_times_confidence

# (summary)
item_times_confidence %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_confidence %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

item_times_confidence %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_confidence %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Item", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_confidence %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_confidence %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)
```


```{r timers per item familiarity}
# all items familiarty timer
item_times_familiarity <- dat %>%
  group_by(item_number, condition) %>%
  summarise(mean = mean(familiarity_timer, na.rm = TRUE), SD = sd(familiarity_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(familiarity_timer, na.rm = TRUE), min = min(familiarity_timer, na.rm = TRUE), max = max(familiarity_timer, na.rm = TRUE))

# item_times_familiarity

# (summary)
item_times_familiarity %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Item", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_familiarity %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

item_times_familiarity %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


item_times_familiarity %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Item", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_familiarity %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Item Non-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)

item_times_familiarity %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = item_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Item With-TP", x = "Item Number", y = "Seconds") +
  facet_wrap(~condition)
```

# Response times per trial 
```{r timers per trial accuracy}
# all trials accuracy timer
trial_times_accuracy <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  summarise(mean = mean(accuracy_timer, na.rm = TRUE), SD = sd(accuracy_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_timer, na.rm = TRUE), min = min(accuracy_timer, na.rm = TRUE), max = max(accuracy_timer, na.rm = TRUE))

# trial_times_accuracy

# (summary)
trial_times_accuracy %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Trial", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

trial_times_accuracy %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

trial_times_accuracy %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


trial_times_accuracy %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Trial", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_accuracy %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_accuracy %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Median Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)
```


```{r timers per trial confidence}
# all trials confidence timer
trial_times_confidence <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  summarise(mean = mean(confidence_timer, na.rm = TRUE), SD = sd(confidence_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(confidence_timer, na.rm = TRUE), min = min(confidence_timer, na.rm = TRUE), max = max(confidence_timer, na.rm = TRUE))

# trial_times_confidence


# (summary)
trial_times_confidence %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Trial", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


trial_times_confidence %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

trial_times_confidence %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


trial_times_confidence %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Trial", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_confidence %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_confidence %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Median Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)
```


```{r timers per trial familiarity}
# all trials familiarty timer
trial_times_familiarity <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  summarise(mean = mean(familiarity_timer, na.rm = TRUE), SD = sd(familiarity_timer, na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(familiarity_timer, na.rm = TRUE), min = min(familiarity_timer, na.rm = TRUE), max = max(familiarity_timer, na.rm = TRUE))

# trial_times_familiarity

# (summary)
trial_times_familiarity %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Trial", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

trial_times_familiarity %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)

trial_times_familiarity %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)


trial_times_familiarity %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Trial", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_familiarity %>%
  dplyr::filter(condition == "Control") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Trial Non-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)

trial_times_familiarity %>%
  dplyr::filter(condition == "Time Pressure") %>%
  ggplot(aes(x = trial_number, y = median)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Median Time Per Trial With-TP", x = "Trial Number", y = "Seconds") +
  facet_wrap(~condition)
```

# changes in value over time
```{r change in scale values over time accuracy }
# all trial accuracy timer
trial_scales_accuracy <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  drop_na(accuracy_response) %>%
  summarise(mean = mean(as.numeric(binary_accuracy), na.rm = TRUE), SD = sd(as.numeric(binary_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(binary_accuracy), na.rm = TRUE), min = min(as.numeric(binary_accuracy), na.rm = TRUE), max = max(as.numeric(binary_accuracy), na.rm = TRUE))

# trial_scales_accuracy

# (summary)
trial_scales_accuracy %>%
  drop_na(trial_number) %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy Mean Scale Value Per Trial", x = "Trial Number", y = "Likert Values (> .5 Accuracy-Yes)") +
  geom_errorbar(aes(ymin = (mean) - se, ymax = (mean) + se), width = .2) +
  facet_wrap(~condition)
```


```{r change in scale values over time confidence}
# all trial confidence timer
trial_scales_confidence <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  drop_na(confidence_response) %>%
  summarise(mean = mean(as.numeric(confidence_response), na.rm = TRUE), SD = sd(as.numeric(confidence_response), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(confidence_response), na.rm = TRUE), min = min(as.numeric(confidence_response), na.rm = TRUE), max = max(as.numeric(confidence_response), na.rm = TRUE))

# trial_scales_confidence

# (summary)
trial_scales_confidence %>%
  drop_na(trial_number) %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Confidence Mean Scale Value Per Trial", x = "Trial Number", y = "Likert Values (> 3 Confidence-Certain)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)
```


```{r change in scale values over time confidence familiarity}
# all trial familiarity timer
trial_scales_familiarity <- dat %>%
  drop_na(trial_number) %>%
  group_by(trial_number, condition) %>%
  drop_na(familiarity_response) %>%
  summarise(mean = mean(as.numeric(binary_familiarity), na.rm = TRUE), SD = sd(as.numeric(binary_familiarity), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(binary_familiarity), na.rm = TRUE), min = min(as.numeric(binary_familiarity), na.rm = TRUE), max = max(as.numeric(binary_familiarity), na.rm = TRUE))

# trial_scales_familiarity

# (summary)
trial_scales_familiarity %>%
  ggplot(aes(x = trial_number, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "familiarity Mean Scale Value Per Trial", x = "Trial Number", y = "Yes/No Values - 1 (> 0.5 Familiar-Yes)") +
  geom_errorbar(aes(ymin = (mean) - se, ymax = (mean) + se), width = .2) +
  facet_wrap(~condition)
```


# Looking into baseline accuracy
```{r baseline accuracy }

# accuracy descriptives all
accuracy <- dat %>%
  drop_na(accuracy_response) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy

# accuracy descriptives group
accuracy_group <- dat %>%
  drop_na(accuracy_response) %>%
  group_by(condition) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy_group

# accuracy descriptives group x political
accuracy_political <- dat %>%
  group_by(condition, political_identity) %>%
  drop_na(accuracy_response) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy_political

# Basic histogram Accuracy scale
dat %>%
  drop_na(part_accuracy) %>%
  ggplot(aes(x = part_accuracy, fill = political_identity)) +
  geom_histogram(stat = "count") +
  theme_apa() +
  labs(title = "Relative Accuracy Histogram", x = "Accuracy (TRUE = correct)", y = "Count") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  facet_wrap(~condition)


# accuracy mean per subject
accuracy_pp <- dat %>%
  group_by(Subject, condition) %>%
  drop_na(accuracy_response) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy_pp

accuracy_pp %>% ggplot(aes(x = Subject, y = mean, fill = condition)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Relative Accuracy Histogram per Subject", x = "Subject", y = "% Corect") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2)

# accuracy mean per item
item_accuracy <- dat %>%
  group_by(item_number, condition) %>%
  drop_na(accuracy_response) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

item_accuracy

item_accuracy %>% ggplot(aes(x = item_number, y = mean, fill)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Relative Accuracy Histogram per Item", x = "Item", y = "% Correct") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~condition)
```


```{r accuracy further}


# accuracy descriptives per second¸
accuracy_bins <- dat %>%
  drop_na(part_accuracy) %>%
  group_by(second_bins) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy_bins

# Basic histogram Accuracy scale
accuracy_bins %>% ggplot(aes(x = second_bins, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Relative Accuracy Histogram", x = "Seconds", y = "% Correct") +
  scale_fill_manual(values = c("#0021F5", "#EA3223")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2)

# accuracy descriptives per second by condition
accuracy_bins_condition <- dat %>%
  drop_na(part_accuracy) %>%
  group_by(second_bins, condition, collection) %>%
  summarise(mean = mean(as.numeric(part_accuracy), na.rm = TRUE), SD = sd(as.numeric(part_accuracy), na.rm = TRUE), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy), na.rm = TRUE), min = min(as.numeric(part_accuracy), na.rm = TRUE), max = max(as.numeric(part_accuracy), na.rm = TRUE))

accuracy_bins_condition

accuracy_bins_condition %>% ggplot(aes(x = second_bins, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Relative Accuracy Histogram", x = "Seconds", y = "% Correct") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_grid(collection ~ condition)

```


```{r running some descriptive stats}

# accuracy_all
accuracy_summary <- dat %>%
  group_by(Subject, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy)))
accuracy_summary <- accuracy_summary %>% mutate(accuracy_percentage = mean * 100)

accuracy_summary <- accuracy_summary %>%
  group_by(condition) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage))


# accuracy and condition
dat %>%
  group_by(condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X Time Pressure", x = "Time Pressure", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2)


# accuracy and condition
dat %>%
  group_by(condition, collection) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X Time Pressure", x = "Time Pressure", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~collection)

# accuracy true and false
dat %>%
  group_by(item_accuracy, collection) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = item_accuracy, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X Item Truthfullness", x = "Item Truthfullness", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~collection)

# accuracy and political identity
dat %>%
  group_by(political_identity, collection) %>%
  drop_na(part_accuracy, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = political_identity, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X Political identity", x = "Political identity", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~collection)

# accuracy and congruency
dat %>%
  group_by(congruency, collection) %>%
  drop_na(part_accuracy, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = congruency, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X Congruency", x = "Congruency", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~collection)

# accuracy and CRT
dat %>%
  group_by(CRT_binary, collection) %>%
  drop_na(part_accuracy, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = CRT_binary, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa() +
  labs(title = "Accuracy X CRT Proficiency", x = "CRT Proficiency", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(~collection)



# accuracy item_accuracy x condition
dat %>%
  group_by(item_accuracy, condition, collection) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = item_accuracy, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "Accuracy X Item Truth X Condition", x = "Item Truthfulness", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_grid(collection ~ condition)

# accuracy item_accuracy x political identity
dat %>%
  group_by(item_accuracy, political_identity, collection) %>%
  drop_na(part_accuracy, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = item_accuracy, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "Accuracy X Item Truth X Political Identity", x = "Item Truthfulness", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_grid(collection ~ political_identity)

# accuracy item_accuracy x congruency
dat %>%
  group_by(item_accuracy, congruency, collection) %>%
  drop_na(part_accuracy, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = item_accuracy, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "Accuracy X Item Truth X Congruency", x = "Item Truthfulness", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(collection ~ congruency)


# accuracy political_identity x CRT_binary
dat %>%
  group_by(political_identity, CRT_binary, collection) %>%
  drop_na(part_accuracy, CRT_binary, political_identity) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  ggplot(aes(x = political_identity, y = mean)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_apa(legend.use.title = TRUE) +
  labs(title = "Accuracy X Political Identity X CRT Proficiency ", x = "Political Identity", y = "Accuracy (%)") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .2) +
  facet_wrap(collection ~ CRT_binary)
```


# figures for paper
## general
```{r figures final 1 - general accuracy}

font_size <- 15

# item_accuracy item and accuracy
TP_descriptive_true_false <- dat %>%
  drop_na(item_accuracy, condition) %>%
  group_by(Subject, item_accuracy, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)


# overall confidence summary stats condition
TP_descriptive_true_false_summary_overall_overall <- dat %>%
  drop_na(item_accuracy, condition, part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

# overall confidence summary stats condition
TP_descriptive_true_false_summary_overall_true_false <- dat %>%
  group_by(item_accuracy) %>%
  drop_na(item_accuracy, condition, part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)


# overall confidence summary stats condition
TP_descriptive_true_false_summary_overall <- TP_descriptive_true_false %>%
  group_by(condition) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage))

# overall confidence summary stats condition
TP_descriptive_true_false_summary <- TP_descriptive_true_false %>%
  group_by(condition, item_accuracy) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage)) %>%
  rename_at(vars(-condition, -item_accuracy), ~ paste0(.x, "_overall_mean"))


TP_descriptive_true_false_plot <-
  TP_descriptive_true_false %>%
ggplot(aes(x = condition, y = accuracy_percentage, fill = item_accuracy)) + 
  ggdist::stat_halfeye(
    # adjust = .5, 
    width = .6, 
    .width = 0, 
    # justification = -.2, 
    point_colour = NA,
    alpha = .25,
    position = position_nudge(x = +.1)
  ) + 
  geom_boxplot(
    width = .1,
    outlier.size = .25,
    # outlier.shape = NA
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    aes(
      color = item_accuracy
      ),
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .5, 
    ## add some transparency
    alpha = .25,
    size = .25,
    position = position_nudge(x = -.01)
  ) +
  geom_pointrange(
    dat = TP_descriptive_true_false_summary,
    aes(
      y = mean_overall_mean,
      ymin = mean_overall_mean - se_overall_mean,
      ymax = mean_overall_mean + se_overall_mean,
      color = item_accuracy
    ),
    size = .25,
    position = position_nudge(x = +.2),
  ) +
  labs(x = "Treatment", y = "Accuracy (%)") +
    theme_apa(legend.use.title = FALSE, legend.pos = "top") +
    theme(text = element_text(size=15)) +
      scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  ylim(0, 100)


TP_descriptive_true_false_plot

ggsave(file= here::here("Figures", "TP_true_false_item.pdf"), plot=TP_descriptive_true_false_plot, width =7, height = 7)
# ggsave(file = "TP_true_false_item_1.pdf", plot = TP_descriptive_true_false_plot, width = 1746, height = 1350, units = c("px"), scale = 1)



```

## CRT
```{r figures final 2 - analytical thinking}

# CRT and accuracy
TP_descriptive_CRT <- dat %>%
  drop_na(item_accuracy, CRT_binary, condition) %>%
  group_by(Subject, item_accuracy, CRT_binary, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_CRT_overall_overall_d <- dat %>%
  drop_na(item_accuracy, CRT_binary, condition,part_accuracy) %>%
  group_by(CRT_binary) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_CRT_overall_overall_time_d <- dat %>%
  drop_na(CRT_binary, condition,part_accuracy) %>%
  group_by(condition, CRT_binary) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_CRT_overall_overall_c <- dat %>%
  drop_na(item_accuracy, CRT_binary, condition,part_accuracy) %>%
  group_by(item_accuracy, CRT_binary) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_CRT_overall_overall_time_c <- dat %>%
  drop_na(item_accuracy, CRT_binary, condition,part_accuracy) %>%
  group_by(item_accuracy, condition, CRT_binary) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

# overall confidence summary stats condition
TP_descriptive_CRT_summary <- TP_descriptive_CRT %>%
  group_by(condition, item_accuracy, CRT_binary) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage)) %>%
  rename_at(vars(-condition, -item_accuracy, -CRT_binary), ~ paste0(.x, "_overall_mean"))


TP_descriptive_CRT_plot <-
  TP_descriptive_CRT %>%
  ggplot(aes(x = CRT_binary, y = accuracy_percentage, fill = item_accuracy)) +
  ggdist::stat_halfeye(
    # adjust = .5, 
    width = .6, 
    .width = 0, 
    # justification = -.2, 
    point_colour = NA,
    alpha = .25,
    position = position_nudge(x = +.1)
  ) + 
  geom_boxplot(
    width = .1,
    outlier.size = .25,
    # outlier.shape = NA
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    aes(
      color = item_accuracy
      ),
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .5, 
    ## add some transparency
    alpha = .25,
    size = .25,
    # make overlap
    position = position_nudge(x = -.01)
  ) +
  geom_pointrange(
    dat = TP_descriptive_CRT_summary,
    aes(
      y = mean_overall_mean,
      ymin = mean_overall_mean - se_overall_mean,
      ymax = mean_overall_mean + se_overall_mean,
      color = item_accuracy
    ),
    size = .25,
    position = position_nudge(x = +.2)
  ) +
  labs(x = "CRT", y = "Accuracy (%)") +
    theme_apa(legend.use.title = FALSE) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  ylim(0, 100) +
  theme(text = element_text(size=15), plot.margin = margin(6, 0, 6, 0)) +
  facet_wrap(~condition)


TP_descriptive_CRT_plot

ggsave(file = here::here("Figures", "TP_CRT.pdf"), plot = TP_descriptive_CRT_plot, width =9, height = 9,dpi = 800)
# ggsave(file="TP_CRT.pdf", plot=TP_descriptive_CRT_plot, width = 750, height = 750, units = c("px"), scale = 1)


```

## ideological congruency
```{r figure 3 - partisan bias}

# partisanship and accuracy
TP_descriptive_congruency <- dat %>%
  drop_na(item_accuracy, congruency, condition) %>%
  group_by(Subject, congruency, item_accuracy, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_congruency_overall_overall_d <- dat %>%
  drop_na(item_accuracy, congruency, condition, part_accuracy) %>%
  group_by(congruency) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_congruency_overall_time_d <- dat %>%
  drop_na(item_accuracy, congruency, condition, part_accuracy) %>%
  group_by(congruency, condition) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_congruency_overall_overall_c <- dat %>%
  drop_na(item_accuracy, congruency, condition, part_accuracy) %>%
  group_by(item_accuracy, congruency) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_congruency_overall_time_c <- dat %>%
  drop_na(item_accuracy, congruency, condition, part_accuracy) %>%
  group_by(item_accuracy, congruency, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)


# overall confidence summary stats condition
TP_descriptive_congruency_summary <- TP_descriptive_congruency %>%
  group_by(condition, item_accuracy, congruency) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage)) %>%
  rename_at(vars(-condition, -item_accuracy, -congruency), ~ paste0(.x, "_overall_mean"))


TP_descriptive_congruency_plot <-
  TP_descriptive_congruency %>%
  ggplot(aes(x = congruency, y = accuracy_percentage, fill = item_accuracy)) +
  ggdist::stat_halfeye(
    # adjust = .5, 
    width = .6, 
    .width = 0, 
    # justification = -.2, 
    point_colour = NA,
    alpha = .25,
    position = position_nudge(x = +.1)
  ) + 
  geom_boxplot(
    width = .1,
    outlier.size = .25,
    # outlier.shape = NA
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    aes(
      color = item_accuracy
      ),
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .5, 
    ## add some transparency
    alpha = .25,
    size = .25,
    # make overlap
    position = position_nudge(x = -.01)
  ) +
  geom_pointrange(
    dat = TP_descriptive_congruency_summary,
    aes(
      y = mean_overall_mean,
      ymin = mean_overall_mean - se_overall_mean,
      ymax = mean_overall_mean + se_overall_mean,
      color = item_accuracy
    ),
    size = .25,
    position = position_nudge(x = +.2)
  ) +
  labs(x = "Ideological Congruency", y = "Accuracy (%)") +
    theme_apa(legend.use.title = FALSE) +
  # theme(legend.position="none") +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  ylim(0, 100) +
  theme(text = element_text(size=15), plot.margin = margin(6, 0, 6, 0)) +
  # theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
  # coord_flip() +
  facet_wrap(~condition)


TP_descriptive_congruency_plot

ggsave(file = here::here("Figures", "TP_Congruency.pdf"), plot = TP_descriptive_congruency_plot, width =9, height = 9,dpi = 800)
# ggsave(file="TP_Congruency.pdf", plot=TP_descriptive_congruency_plot, width = 750, height = 750, units = c("px"), scale = 1)


```

```{r combining first two predictor graphs into one image}

# arrange the three plots in a single row
CRT_congruency_predictor_final_figures <- 
  cowplot::plot_grid(
  TP_descriptive_CRT_plot + theme(legend.position="none", text = element_text(size=15)),
  TP_descriptive_congruency_plot + theme(legend.position="none", text = element_text(size=15)),
  # align = 'vh',
  labels = c("A", "B"),
  # hjust = -1,
  nrow = 2
)

# extract a legend that is laid out horizontally
legend_b <- get_legend(
  TP_descriptive_CRT_plot + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
CRT_congruency_predictor_final_figures <- cowplot::plot_grid(CRT_congruency_predictor_final_figures, legend_b, ncol = 1, rel_heights = c(1, .1))


ggsave(file = here::here("Figures", "CRT_congruency_predictor_final_figures.pdf"), 
       plot = CRT_congruency_predictor_final_figures,
  width = 8,
  height = 12
  )

```


## motivated reasoning
```{r figure 6 - motivated reasoning}

# motivated reasoning and accuracy
TP_descriptive_motivated <- dat %>%
  drop_na(item_accuracy, congruency, CRT_binary, condition) %>%
  group_by(Subject, congruency, item_accuracy, condition, CRT_binary) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_motivated_overall_overall_d <- dat %>%
  drop_na(item_accuracy, congruency, CRT_binary, condition, part_accuracy) %>%
  group_by(congruency, CRT_binary) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_motivated_overall_time_d <- dat %>%
  drop_na(item_accuracy, congruency, CRT_binary, condition, part_accuracy) %>%
  group_by(congruency, CRT_binary, condition) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

# overall confidence summary stats condition
TP_descriptive_motivated_summary <- TP_descriptive_motivated %>%
  group_by(condition, item_accuracy, congruency, CRT_binary) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage)) %>%
  rename_at(vars(-condition, -item_accuracy, -congruency, -CRT_binary), ~ paste0(.x, "_overall_mean"))


TP_descriptive_motivated_plot <-
  TP_descriptive_motivated %>%
  ggplot(aes(x = congruency, y = accuracy_percentage, fill = item_accuracy)) +
  ggdist::stat_halfeye(
    # adjust = .5, 
    width = .6, 
    .width = 0, 
    # justification = -.2, 
    point_colour = NA,
    alpha = .25,
    position = position_nudge(x = +.1)
  ) + 
  geom_boxplot(
    width = .1,
    outlier.size = .25,
    # outlier.shape = NA
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    aes(
      color = item_accuracy
      ),
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .5, 
    ## add some transparency
    alpha = .25,
    size = .25,
    # make overlap
    position = position_nudge(x = -.01)
  ) +
  geom_pointrange(
    dat = TP_descriptive_motivated_summary,
    aes(
      y = mean_overall_mean,
      ymin = mean_overall_mean - se_overall_mean,
      ymax = mean_overall_mean + se_overall_mean,
      color = item_accuracy
    ),
    size = .25,
    position = position_nudge(x = +.2)
  ) +
  labs(x = "Ideological Congruency", y = "Accuracy (%)") +
    theme_apa(legend.use.title = FALSE) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  ylim(0, 100) +
  theme(text = element_text(size=15), plot.margin = margin(6, 0, 6, 0)) +
  # theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
  # coord_flip() +
  facet_grid(CRT_binary ~ condition)


TP_descriptive_motivated_plot

ggsave(file = here::here("Figures", "TP_Motivated.pdf"), plot = TP_descriptive_motivated_plot)
# ggsave(file="TP_familiarity.pdf", plot=TP_descriptive_motivated_plot, width = 750, height = 750, units = c("px"), scale = 1)

```

## familiarity
```{r figure 5 - familiarity}

# familiarity and accuracy
TP_descriptive_familiarity <- dat %>%
  drop_na(item_accuracy, familiarity_response, condition) %>%
  group_by(Subject, familiarity_response, item_accuracy, condition) %>%
  drop_na(part_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_familiarity_overall <- dat %>%
  drop_na(item_accuracy, familiarity_response, condition, part_accuracy) %>%
  group_by(familiarity_response, condition) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_familiarity_overall_item <- dat %>%
  drop_na(item_accuracy, familiarity_response, condition, part_accuracy) %>%
  group_by(familiarity_response, item_accuracy) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)

TP_descriptive_familiarity_overall_time <- dat %>%
  drop_na(item_accuracy, familiarity_response, condition, part_accuracy) %>%
  group_by(familiarity_response, item_accuracy, condition) %>%
  summarise(mean = mean(as.numeric(part_accuracy)), SD = sd(as.numeric(part_accuracy)), count = n(), se = (SD / (sqrt(count))), median = median(as.numeric(part_accuracy)), min = min(as.numeric(part_accuracy)), max = max(as.numeric(part_accuracy))) %>%
  mutate(accuracy_percentage = mean * 100)


# overall confidence summary stats condition
TP_descriptive_familiarity_summary <- TP_descriptive_familiarity %>%
  group_by(condition, item_accuracy, familiarity_response) %>%
  summarise(mean = mean(accuracy_percentage), SD = sd(accuracy_percentage), count = n(), se = (SD / (sqrt(count))), median = median(accuracy_percentage), min = min(accuracy_percentage), max = max(accuracy_percentage)) %>%
  rename_at(vars(-condition, -item_accuracy, -familiarity_response), ~ paste0(.x, "_overall_mean"))


TP_descriptive_familiarity_plot <-
  TP_descriptive_familiarity %>%
  ggplot(aes(x = familiarity_response, y = accuracy_percentage, fill = item_accuracy)) +
  ggdist::stat_halfeye(
    # adjust = .5, 
    width = .6, 
    .width = 0, 
    # justification = -.2, 
    point_colour = NA,
    alpha = .25,
    position = position_nudge(x = +.1)
  ) + 
  geom_boxplot(
    width = .1,
    outlier.size = .25,
    # outlier.shape = NA
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    aes(
      color = item_accuracy
      ),
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .5, 
    ## add some transparency
    alpha = .25,
    size = .25,
    # make overlap
    position = position_nudge(x = -.01)
  ) +
  geom_pointrange(
    dat = TP_descriptive_familiarity_summary,
    aes(
      y = mean_overall_mean,
      ymin = mean_overall_mean - se_overall_mean,
      ymax = mean_overall_mean + se_overall_mean,
      color = item_accuracy
    ),
    size = .25,
    position = position_nudge(x = +.2)
  ) +
  labs(x = "Familiarity", y = "Accuracy (%)") +
    theme_apa(legend.use.title = FALSE) +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  ylim(0, 100) +
  theme(text = element_text(size=15), plot.margin = margin(6, 0, 6, 0)) +
  # theme(axis.text.y = element_text(angle = 90, hjust = 0.5)) +
  # coord_flip() +
  facet_wrap(~condition)


TP_descriptive_familiarity_plot

ggsave(file = here::here("Figures", "TP_familiarity.pdf"), plot = TP_descriptive_familiarity_plot)
# ggsave(file="TP_familiarity.pdf", plot=TP_descriptive_familiarity_plot, width = 750, height = 750, units = c("px"), scale = 1)


familiarity_response_plot <- TP_descriptive_familiarity_overall_time %>%
    ggplot(aes(x = familiarity_response, y = count, fill = item_accuracy)) +
    geom_bar(stat = "identity") +
    theme_apa() +
    theme(text = element_text(size=15)) +
    labs(x = "Familiarity", y = "Count") +
      scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
  facet_wrap(~condition)

ggsave(file = here::here("Figures", "familiarity_response.pdf"), plot = familiarity_response_plot, width = 7, height = 4.5)

familiarity_response_plot


```


```{r combining first two predictor graphs into one image}

# arrange the three plots in a single row
prior_exposure_motivated_predictor_final_figures <- 
  cowplot::plot_grid(
  TP_descriptive_motivated_plot + theme(legend.position="none", text = element_text(size=15)),
  TP_descriptive_familiarity_plot + theme(legend.position="none", text = element_text(size=15)),
  # align = 'vh',
  labels = c("A", "B"),
  # hjust = -1,
  nrow = 2
)

# extract a legend that is laid out horizontally
legend_b <- get_legend(
  TP_descriptive_motivated_plot + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
prior_exposure_motivated_predictor_final_figures <- cowplot::plot_grid(prior_exposure_motivated_predictor_final_figures, legend_b, ncol = 1, rel_heights = c(1, .1))

ggsave(file = here::here("Figures", "prior_exposure_motivated_predictor_final_figures.pdf"), 
       plot = prior_exposure_motivated_predictor_final_figures,
  width = 8,
  height = 12
  )


```



```{r combining graphs into one image}

all_final_figures <- ggarrange(TP_descriptive_CRT_plot, TP_descriptive_congruency_plot, TP_descriptive_familiarity_plot, TP_descriptive_motivated_plot, ncol=2, nrow=2, common.legend = TRUE, legend="bottom")

ggsave(file = here::here("Figures", "all_predictor_final_figures.pdf"), plot = all_final_figures, width = 10, height = 14)

```



# models
```{r final models manuscript centralised - TP}
# model with time pressure
model.accuracy.time.bays <- brm(formula = accuracy_response ~ C_item_accuracy*CRT_standard*condition_num +
                                  C_item_accuracy*C_congruency_non_binary*CRT_standard*condition_num +
                                  C_item_accuracy*familiarity_response*condition_num +
                                  (1 | ID) +
                                  (1 | item_number),
                                data = dat,
                                family = bernoulli(link = "probit"),
                                iter = 10000,
                                cores = getOption("mc.cores", 4),
                                file = here::here("Models",  "model"),
                                )

# summary
# summary(model.accuracy.time.bays)

# parameters
# model_parameters <- c("b_Intercept",                                            
# "b_C_item_accuracy",                                      
# "b_CRT_standard",                                         
# "b_condition_num1",                                          
# "b_C_congruency_non_binary",                                         
# "b_familiarity_responseYes",                              
# "b_C_item_accuracy:CRT_standard",                         
# "b_C_item_accuracy:condition_num1",                          
# "b_CRT_standard:condition_num1",                             
#  "b_C_item_accuracy:C_congruency_non_binary",                         
#  "b_CRT_standard:C_congruency_non_binary",                            
#  "b_condition_num1:C_congruency_non_binary",                             
#  "b_C_item_accuracy:familiarity_responseYes",              
#  "b_condition_num1:familiarity_responseYes",                  
#  "b_C_item_accuracy:CRT_standard:condition_num1",             
#  "b_C_item_accuracy:CRT_standard:C_congruency_non_binary",            
#  "b_C_item_accuracy:condition_num1:C_congruency_non_binary",             
#  "b_CRT_standard:condition_num1:C_congruency_non_binary",                
#  "b_C_item_accuracy:condition_num1:familiarity_responseYes",  
#  "b_C_item_accuracy:CRT_standard:condition_num1:C_congruency_non_binary")

# mcmc_plot(model.accuracy.time.bays,
#   type = "trace"
#   # , variable = model_parameters[1:12]
# )


# mcmc_plot(model.accuracy.time.bays, type = "intervals")
# mcmc_plot(model.accuracy.time.bays, type = "dens")


###### Stuff added by Alan ######

#The idea is to analyse the chains yourself.
#Thus, first you get the draws
draws <- posterior_samples(model.accuracy.time.bays)

#Then, you calculate the new variables (there should be a better way, but this worked)
draws <- draws %>% mutate(`b_condition_num1` = b_condition_num1 + b_Intercept,
                 `b_CRT_standard:condition_num1` = `b_CRT_standard:condition_num1` + b_CRT_standard,
                 `b_condition_num1:C_congruency_non_binary` = `b_condition_num1:C_congruency_non_binary` + b_C_congruency_non_binary, 
                 `b_condition_num1:familiarity_responseYes` = `b_condition_num1:familiarity_responseYes` + b_familiarity_responseYes,
                 `b_CRT_standard:condition_num1:C_congruency_non_binary` = `b_CRT_standard:condition_num1:C_congruency_non_binary` + `b_CRT_standard:C_congruency_non_binary`,
                 
                 `b_C_item_accuracy:condition_num1` = `b_C_item_accuracy:condition_num1` + b_C_item_accuracy,
                 `b_C_item_accuracy:CRT_standard:condition_num1` = `b_C_item_accuracy:CRT_standard:condition_num1` + `b_C_item_accuracy:CRT_standard`,
                 `b_C_item_accuracy:condition_num1:C_congruency_non_binary` = `b_C_item_accuracy:condition_num1:C_congruency_non_binary` + `b_C_item_accuracy:C_congruency_non_binary`,
                 `b_C_item_accuracy:condition_num1:familiarity_responseYes` = `b_C_item_accuracy:condition_num1:familiarity_responseYes` + `b_C_item_accuracy:familiarity_responseYes`,
                 `b_C_item_accuracy:CRT_standard:condition_num1:C_congruency_non_binary` = `b_C_item_accuracy:CRT_standard:condition_num1:C_congruency_non_binary` + `b_C_item_accuracy:CRT_standard:C_congruency_non_binary`)

estimates <- apply(draws,2,mean)

upper <- apply(draws,2,quantile,probs=0.975)
lower <- apply(draws,2,quantile,probs=0.025)

model_coefs <- data.frame(estimates,lower,upper) #the new coefficients

# changing colnames
model_coefs$predictor <- rownames(model_coefs)

# removing b from names
model_coefs$predictor <- str_replace_all(model_coefs$predictor, "b_", "")

# shortening df
model_coefs <- model_coefs[1:20,]
rownames(model_coefs) <- seq(1, length(model_coefs$predictor), 1)


# #E.g., the bias is stronger in control:
# model_coefs["b_Intercept",]
# model_coefs["b_condition_num1",]
# 
# #and d' is lower under time pressure:
# model_coefs["b_C_item_accuracy",]
# model_coefs["raw_d_tp",]


###### END ######

model.summary <- summary(model.accuracy.time.bays)
# model.summary

model_coefs_predictor <- model.summary[["fixed"]]
# tmp <- model_coefs_predictor

# changing colnames
model_coefs_predictor$predictor <- rownames(model_coefs_predictor)

# checking if predictors on model_coefs match model_coefs_predictor
table(model_coefs_predictor$predictor == model_coefs$predictor)

# adding additive to difference based output
model_coefs_predictor <- model_coefs_predictor %>%
  mutate(estimate_additive = model_coefs$estimates,
    lower_additive = model_coefs$lower,
    upper_additive = model_coefs$upper
         )

rownames(model_coefs_predictor) <- seq(1, length(model_coefs_predictor$estimate), 1)

model_coefs_predictor$predictor <- str_replace_all(model_coefs_predictor$predictor, "C_", "")

# changing accuracy item to d_prime
model_coefs_predictor <- 
  model_coefs_predictor %>% 
  mutate(
  predictor = str_replace_all(predictor, "item_accuracy", "d_prime"),
  predictor = str_replace_all(predictor, "Intercept", "response_bias"),
  predictor = str_replace_all(predictor, "condition_num1", "time_treat"),
  predictor = str_replace_all(predictor, "CRT_standard", "CRT"),
  predictor = str_replace_all(predictor, "familiarity_response", "familiarity"),
  predictor = str_replace_all(predictor, "congruency_non_binary", "congruency")
  )


# adding response_bias to time_treat
model_coefs_predictor$predictor[model_coefs_predictor$predictor == "time_treat"] <- "response_bias:time_treat"

plot_levels <- c("d_prime", #d'
                 "d_prime:time_treat", #tp on d'
                 
                 "response_bias", #c
                 "response_bias:time_treat", #tp on c

                 
          "d_prime:CRT", #d'
          "d_prime:CRT:time_treat", #tp on d'
          "CRT", #c
          "CRT:time_treat", #tp on c
          
          
          "d_prime:congruency", #d'
          "d_prime:time_treat:congruency", #tp on d'
          "congruency", #ç
          "time_treat:congruency", #tp on c
          
          
          "d_prime:CRT:congruency", #d'
          "d_prime:CRT:time_treat:congruency", #tp on d'
          "CRT:congruency", #c
          "CRT:time_treat:congruency", #tp on c
          
          
          "d_prime:familiarityYes", #d'
          "d_prime:time_treat:familiarityYes", #tp on d'
          "familiarityYes", #c
          "time_treat:familiarityYes" #tp on c
          
          )


model_coefs_predictor <- model_coefs_predictor %>% rename(estimate = Estimate, lower = `l-95% CI`, upper = `u-95% CI`)

# chagning class
# model_coefs_predictor$predictor <- factor(model_coefs_predictor$predictor, levels = rev(plot_levels))


model_coefs_predictor <- 
  model_coefs_predictor %>% 
  mutate(
  SDT = ifelse(str_detect(predictor, "d_prime"), "d_prime", "Response Bias"),
  Treatment = ifelse(str_detect(predictor, "time_treat") & str_detect(SDT, "d_prime"), "Time Pressure", 
                 ifelse(str_detect(predictor, "time_treat") & str_detect(SDT, "Response Bias"), "Time Pressure", "Control")
                 )
  )


# removing d_prime and time_treat from predictor
model_coefs_predictor$predictor <- as.character(model_coefs_predictor$predictor)

model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)] <- str_replace(model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)], "d_prime:", "")

model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)] <- str_replace(model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)], ":d_prime", "")

model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)] <- str_replace(model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)], "time_treat:", "")

model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)] <- str_replace(model_coefs_predictor$predictor[3:length(model_coefs_predictor$predictor)], ":time_treat", "")

# the last time treat is d' time treat. 
model_coefs_predictor$predictor <- str_replace(model_coefs_predictor$predictor, "time_treat", "d_prime")


# adding baseline
model_coefs_predictor$predictor <- str_replace_all(model_coefs_predictor$predictor, "d_prime", "baseline")
model_coefs_predictor$predictor <- str_replace_all(model_coefs_predictor$predictor, "response_bias", "baseline")


# changing to factor again
model_coefs_predictor$predictor <- factor(model_coefs_predictor$predictor, levels = rev(c("baseline", "CRT", "congruency", "CRT:congruency",  "familiarityYes")))


model_coefs_predictor$SDT <- str_replace_all(model_coefs_predictor$SDT, "d_prime", "Discrimination Ability")
model_coefs_predictor$SDT <- factor(model_coefs_predictor$SDT, levels = c("Discrimination Ability", "Response Bias"))


model_coefs_predictor$Treatment <- factor(model_coefs_predictor$Treatment, levels = c("Control", "Time Pressure"))
  

# plot
model_coefs_predictor_plot <- model_coefs_predictor %>% 
  ggplot(aes(x = predictor, y = estimate_additive, color = Treatment)) +
   geom_hline(yintercept = 0, linetype="dotted", 
                color = "grey", size=.25) +
   geom_pointrange(aes(ymin = lower_additive,
       ymax = upper_additive),
       position = position_dodge(-0.5)) + 
  labs(x= "Coefficients", y= "Estimates") +
  scale_color_manual(values = c("black","darkgrey")) +
  coord_flip() +
  theme_apa() +
  theme(legend.pos = "bottom", text = element_text(size=15)) +
  facet_grid(~SDT, scales="free_y") 


model_coefs_predictor_plot



# plot_grid(model_coefs_predictor_plot_d, model_coefs_predictor_plot_c) 
# prior_exposure_motivated_predictor_final_figures <- 
  # ggarrange(model_coefs_predictor_plot_d, model_coefs_predictor_plot_c, ncol=1, nrow=2)

# save plot
ggsave(file = here::here("Figures", "regression_coeffs_plot.pdf"), plot = model_coefs_predictor_plot, width =7, height = 4.5)
# model_coefs_predictor$estimate <- as.numeric(model_coefs_predictor$estimate)

# saving models as tables
# texreg(model.accuracy.time.bays, file = "model.manuscript.tex")

# sjPlot::tab_model(model.criterion.bays, file = "model.accuracy.time.manuscript.NTP.doc")
# sjPlot::tab_model(model.accuracy.time.bays, file = "model.accuracy.time.manuscript.TP.doc")
# plot_model(model.criterion.bays, type = "re")
```


```{r final models manuscript centralised with familiarity centralised also - TP}
# model with time pressure (through 1)
model.accuracy.time.bays.familiar <- brm(accuracy_response ~
                                           C_item_accuracy*CRT_standard*condition_num +
                                           C_item_accuracy*C_congruency_non_binary*CRT_standard*condition_num +
                                           C_item_accuracy*C_familiarity_response*condition_num +
                                           (1 | ID) +
                                           (1 | item_number),
                                         data = dat,
                                         family = bernoulli(link = "probit"),
                                         iter = 10000,
                                         cores = getOption("mc.cores", 4),
                                         file = here::here("Models", "model.familiar.center")
                                         )

# summary
# summary(model.accuracy.time.bays.familiar)

# mcmc_plot(model.accuracy.time.bays.familiar,
  # type = "trace"
# )

# mcmc_plot(model.accuracy.time.bays.familiar, type = "intervals")
# mcmc_plot(model.accuracy.time.bays.familiar, type = "dens")


###### Stuff added by Alan ######

#The idea is to analyse the chains yourself.
#Thus, first you get the draws
draws.familiar <- posterior_samples(model.accuracy.time.bays.familiar)

#Then, you calculate the new variables (there should be a better way, but this worked)
draws.familiar <- draws.familiar %>% mutate(`b_condition_num1` = b_condition_num1 + b_Intercept,
                 `b_CRT_standard:condition_num1` = `b_CRT_standard:condition_num1` + b_CRT_standard,
                 `b_condition_num1:C_congruency_non_binary` = `b_condition_num1:C_congruency_non_binary` + b_C_congruency_non_binary, 
                 `b_condition_num1:C_familiarity_response` = `b_condition_num1:C_familiarity_response` + b_C_familiarity_response,
                 `b_CRT_standard:condition_num1:C_congruency_non_binary` = `b_CRT_standard:condition_num1:C_congruency_non_binary` + `b_CRT_standard:C_congruency_non_binary`,
                 
                 `b_C_item_accuracy:condition_num1` = `b_C_item_accuracy:condition_num1` + b_C_item_accuracy,
                 `b_C_item_accuracy:CRT_standard:condition_num1` = `b_C_item_accuracy:CRT_standard:condition_num1` + `b_C_item_accuracy:CRT_standard`,
                 `b_C_item_accuracy:condition_num1:C_congruency_non_binary` = `b_C_item_accuracy:condition_num1:C_congruency_non_binary` + `b_C_item_accuracy:C_congruency_non_binary`,
                 `b_C_item_accuracy:condition_num1:C_familiarity_response` = `b_C_item_accuracy:condition_num1:C_familiarity_response` + `b_C_item_accuracy:C_familiarity_response`,
                 `b_C_item_accuracy:CRT_standard:condition_num1:C_congruency_non_binary` = `b_C_item_accuracy:CRT_standard:condition_num1:C_congruency_non_binary` + `b_C_item_accuracy:CRT_standard:C_congruency_non_binary`)

estimates.familiar <- apply(draws.familiar,2,mean)

upper.familiar <- apply(draws.familiar,2,quantile,probs=0.975)
lower.familiar <- apply(draws.familiar,2,quantile,probs=0.025)

model_coefs.familiar <- data.frame(estimates.familiar,lower.familiar,upper.familiar) #the new coefficients

# changing colnames
model_coefs.familiar$predictor <- rownames(model_coefs.familiar)

# removing b from names
model_coefs.familiar$predictor <- str_replace_all(model_coefs.familiar$predictor, "b_", "")

# shortening df
model_coefs.familiar <- model_coefs.familiar[1:20,]
rownames(model_coefs.familiar) <- seq(1, length(model_coefs.familiar$predictor), 1)


# #E.g., the bias is stronger in control:
# model_coefs.familiar["b_Intercept",]
# model_coefs.familiar["b_condition_num1",]
# 
# #and d' is lower under time pressure:
# model_coefs.familiar["b_C_item_accuracy",]
# model_coefs.familiar["raw_d_tp",]


###### END ######

model.summary.familiar <- summary(model.accuracy.time.bays.familiar)
# model.summary.familiar

model_coefs_predictor.familiar <- model.summary.familiar[["fixed"]]
# tmp <- model_coefs_predictor

# changing colnames
model_coefs_predictor.familiar$predictor <- rownames(model_coefs_predictor.familiar)

# checking if predictors on model_coefs match model_coefs_predictor
table(model_coefs_predictor.familiar$predictor == model_coefs.familiar$predictor)

# adding additive to difference based output
model_coefs_predictor.familiar <- model_coefs_predictor.familiar %>%
  mutate(estimate_additive = model_coefs.familiar$estimates,
    lower_additive = model_coefs.familiar$lower,
    upper_additive = model_coefs.familiar$upper
         )

rownames(model_coefs_predictor.familiar) <- seq(1, length(model_coefs_predictor.familiar$estimate), 1)

model_coefs_predictor.familiar$predictor <- str_replace_all(model_coefs_predictor.familiar$predictor, "C_", "")

# changing accuracy item to d_prime
model_coefs_predictor.familiar <- 
  model_coefs_predictor.familiar %>% 
  mutate(
  predictor = str_replace_all(predictor, "item_accuracy", "d_prime"),
  predictor = str_replace_all(predictor, "Intercept", "response_bias"),
  predictor = str_replace_all(predictor, "condition_num1", "time_treat"),
  predictor = str_replace_all(predictor, "CRT_standard", "CRT"),
  predictor = str_replace_all(predictor, "familiarity_response", "familiarity"),
  predictor = str_replace_all(predictor, "congruency_non_binary", "congruency")
  )

# adding response_bias to time_treat
model_coefs_predictor.familiar$predictor[model_coefs_predictor.familiar$predictor == "time_treat"] <- "response_bias:time_treat"

plot_levels <- c("d_prime", #d'
                 "d_prime:time_treat", #tp on d'
                 
                 "response_bias", #c
                 "response_bias:time_treat", #tp on c

                 
          "d_prime:CRT", #d'
          "d_prime:CRT:time_treat", #tp on d'
          "CRT", #c
          "CRT:time_treat", #tp on c
          
          
          "d_prime:congruency", #d'
          "d_prime:time_treat:congruency", #tp on d'
          "congruency", #ç
          "time_treat:congruency", #tp on c
          
          
          "d_prime:CRT:congruency", #d'
          "d_prime:CRT:time_treat:congruency", #tp on d'
          "CRT:congruency", #c
          "CRT:time_treat:congruency", #tp on c
          
          
          "d_prime:familiarity", #d'
          "d_prime:time_treat:familiarity", #tp on d'
          "familiarity", #c
          "time_treat:familiarity" #tp on c
          
          )


model_coefs_predictor.familiar <- model_coefs_predictor.familiar %>% rename(estimate = Estimate, lower = `l-95% CI`, upper = `u-95% CI`)

# chagning class
# model_coefs_predictor.familiar$predictor <- factor(model_coefs_predictor.familiar$predictor, levels = rev(plot_levels))

model_coefs_predictor.familiar <- 
  model_coefs_predictor.familiar %>% 
  mutate(
  SDT = ifelse(str_detect(predictor, "d_prime"), "d_prime", "Response Bias"),
  Treatment = ifelse(str_detect(predictor, "time_treat") & str_detect(SDT, "d_prime"), "Time Pressure", 
                 ifelse(str_detect(predictor, "time_treat") & str_detect(SDT, "Response Bias"), "Time Pressure", "Control"))
  )

# removing d_prime and time_treat from predictor
model_coefs_predictor.familiar$predictor <- as.character(model_coefs_predictor.familiar$predictor)

model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)] <- str_replace(model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)], "d_prime:", "")

model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)] <- str_replace(model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)], ":d_prime", "")

model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)] <- str_replace(model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)], "time_treat:", "")

model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)] <- str_replace(model_coefs_predictor.familiar$predictor[3:length(model_coefs_predictor.familiar$predictor)], ":time_treat", "")

# the last time treat is d' time treat. 
model_coefs_predictor.familiar$predictor <- str_replace(model_coefs_predictor.familiar$predictor, "time_treat", "d_prime")


# adding baseline
model_coefs_predictor.familiar$predictor <- str_replace_all(model_coefs_predictor.familiar$predictor, "d_prime", "baseline")
model_coefs_predictor.familiar$predictor <- str_replace_all(model_coefs_predictor.familiar$predictor, "response_bias", "baseline")


# changing to factor again
model_coefs_predictor.familiar$predictor <- factor(model_coefs_predictor.familiar$predictor, levels = rev(c("baseline", "CRT", "congruency", "CRT:congruency",  "familiarity")))

model_coefs_predictor.familiar$SDT <- str_replace_all(model_coefs_predictor.familiar$SDT, "d_prime", "Discrimination Ability")
model_coefs_predictor.familiar$SDT <- factor(model_coefs_predictor.familiar$SDT, c("Discrimination Ability", "Response Bias"))

model_coefs_predictor.familiar$Treatment <- factor(model_coefs_predictor.familiar$Treatment, levels = c("Control", "Time Pressure"))


# plot
model_coefs_predictor_plot.familiar <- model_coefs_predictor.familiar %>% 
  ggplot(aes(x = predictor, y = estimate_additive, color = Treatment)) +
   geom_hline(yintercept = 0, linetype="dotted", 
                color = "grey", size=.25) +
   geom_pointrange(aes(ymin = lower_additive,
       ymax = upper_additive),
       position = position_dodge(-0.5)) + 
  labs(x= "Coefficients", y= "Estimates") +
  scale_color_manual(values = c("black","darkgrey")) +
  coord_flip() +
  theme_apa() +
  theme(legend.pos = "bottom", text = element_text(size=15)) +
  facet_grid(~SDT, scales="free_y") 

# theme(text = element_text(size=10))

model_coefs_predictor_plot.familiar


# save plot
ggsave(file = here::here("Figures", "regression_coeffs_plot.familiar.pdf"), plot = model_coefs_predictor_plot.familiar, width = 7, height = 4.5)


# saving models as tables
# texreg(model.accuracy.time.bays.familiar, file = "model.accuracy.time.manuscript.TP.tex")

# sjPlot::tab_model(model.criterion.bays, file = "model.accuracy.time.manuscript.NTP.doc")
# sjPlot::tab_model(model.accuracy.time.bays.familiar, file = "model.accuracy.time.manuscript.TP.doc")
# plot_model(model.criterion.bays, type = "re")
```



