---
title: "Making Dataset"
author: "Mubashir Sultan"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries and initial setup,  include=FALSE}
# loading libraries
library(here)
library(readxl)
library(writexl)
library(tidyverse)


```


The final dataset comprises of three datasets (collection times) which have been merged and prolific ids anonomised. the df that is loaded next has hence merged and anonomised the dfs.

```{r load df}

df_all <- read_excel(here::here("Data", "Raw", "raw_data.xlsx"), sheet = 1, col_names = TRUE, col_types = NULL)

```


data that is collected but not needed for analysis 
```{r not needed}

#  removing variables that are not needed
not_needed <- c("backbutton", 
                "nextbutton",
                "nt_browser_type",
                "nt_browser_with_version",
                "nt_now",
                "nt_operating_system",
                "nt_precision",
                "nt_RAF",
                "nt_screen_height",
                "nt_screen_width",
                "nt_session_state",
                "nt_screen_state",
                "nt_window_height",
                "nt_window_width", 
                "scaleQuestionOne", 
                "scaleQuestionTwo", 
                "scaleQuestionThree", 
                "scaleQuestionFour", 
                "scaleQuestionFive", 
                "scaleQuestionSix", 
                "scaleQuestionSeven", 
                "scaleQuestionEight", 
                "securityMeasure",
                "SESSION_ID", 
                "STUDY_ID",
                "items_correct",
                "trial_images_first",
                "trial_images_second",
                "screen_order",
                "trial_order_block1",
                "item_order_block1",
                "trial_order_block2",
                "item_order_block2",
                "rand_shuffle_buttons",
                "understoodnButton",
                "consentButton",
                "nextButtonConsent",
                "comp_check_counter1",
                "comp_check_counter2",
                "comp_check_counter3",
                "comp_check_counter4",
                "trial_number_practice_trial",
                "accuracy_timer_practice_trial",
                "accuracy_scale_practice_trial",
                "familarity_scale_practice_trial",
                "confidence_timer_practice_trial",
                "confidence_scale_practice_trial",
                "familarity_timer_practice_trial")


# removing not needed
df_all <- df_all %>% dplyr::filter(!Name %in% not_needed)

```


adding a participant identifier that starts off participant number at 1

```{r unique identifier}

# removing unnecessary columns data
df_all_1 <- df_all[, 5:7]


# adding ID number column relative to subject number
df_all_1$ID <- df_all_1$Subject
unique_subjects <- unique(df_all_1$Subject)
number_subjects <- seq(1,length(unique_subjects), 1)

for (i in 1:length(unique_subjects)) {
  
  df_all_1$ID[df_all_1$Subject == unique_subjects[i]] <- number_subjects[i]

}

# re-ordering rows
# rownames(df_all_1) <- seq(1, length(df_all_1$Subject), 1)

#sort by submission id. 
# df_all_1 <- df_all_1[order(df_all_1$Subject),]

df_all <- df_all_1

```


837 participants in total to begin with.
```{r changing to wide format}

# changing to wide format
df_all <- df_all %>% pivot_wider(names_from = Name, values_from = Value, id_cols = c(ID, Subject))

```


```{r making df tidy ready,  include=FALSE}
# long format
df_all.long <- pivot_longer(df_all, !c("Subject", "ID", "PROLIFIC_PID", "timerFirstBlock", "timerSecondBlock", "age", "gender", "political_identification_scale", "support_biden", "support_trump", "optionalFeedback", "overallTime", "CRT_1", "CRT_2", "CRT_3", "CRT_4", "CRT_5", "condition", "collection", "political_interest_1", "political_interest_2", "news_consumption_1", "news_consumption_2", "bonus"), names_to = "measurement", values_to = "value")

# seems like there is a minor error with how measurement for item number 116 and 173 have been encoded via the experiment (only for trial number). they are flipped. so i will re-flip them now.
df_all.long$measurement <- str_replace_all(df_all.long$measurement, "trial_number_116", "trial_number_one_one_six")
df_all.long$measurement <- str_replace_all(df_all.long$measurement, "trial_number_173", "trial_number_one_seven_three")
df_all.long$measurement <- str_replace_all(df_all.long$measurement, "trial_number_one_one_six", "trial_number_173")
df_all.long$measurement <- str_replace_all(df_all.long$measurement, "trial_number_one_seven_three", "trial_number_116")

# this long format has very many data that are not required, so only keeping those that are needed. plus all the relevant data is in two columns and we don't want that, so i will break these apart now too (they should all be the same length. we can then join).

# accuracy scale
df_all.long.accuracy_scale <- df_all.long %>% filter(
  str_detect(measurement, "accuracy_scale_")
)
# adding columns names so they stay discernible
colnames(df_all.long.accuracy_scale)[colnames(df_all.long.accuracy_scale) == "value"] <- "accuracy_scale"

# keeping the relevant columns in mind after the first df (accuracy_scale).
# accuracy timer
df_all.long.accuracy_timer <- df_all.long %>% filter(
  str_detect(measurement, "accuracy_timer_")
)
colnames(df_all.long.accuracy_timer)[colnames(df_all.long.accuracy_timer) == "value"] <- "accuracy_timer"
df_all.long.accuracy_timer <- df_all.long.accuracy_timer[, c("ID", "measurement", "accuracy_timer")]


# confidence scale
df_all.long.confidence_scale <- df_all.long %>% filter(
  str_detect(measurement, "confidence_scale_")
)
colnames(df_all.long.confidence_scale)[colnames(df_all.long.confidence_scale) == "value"] <- "confidence_scale"
df_all.long.confidence_scale <- df_all.long.confidence_scale[, c("ID", "measurement", "confidence_scale")]
  
  
# confidence timer
df_all.long.confidence_timer <- df_all.long %>% filter(
  str_detect(measurement, "confidence_timer_")
)
colnames(df_all.long.confidence_timer)[colnames(df_all.long.confidence_timer) == "value"] <- "confidence_timer"
df_all.long.confidence_timer <- df_all.long.confidence_timer[, c("ID", "measurement", "confidence_timer")]


# familarity scale
df_all.long.familarity_scale <- df_all.long %>% filter(
  str_detect(measurement, "familarity_scale_")
)
colnames(df_all.long.familarity_scale)[colnames(df_all.long.familarity_scale) == "value"] <- "familarity_scale"
df_all.long.familarity_scale <- df_all.long.familarity_scale[, c("ID", "measurement", "familarity_scale")]

  
# familarity timer
df_all.long.familarity_timer <- df_all.long %>% filter(
  str_detect(measurement, "familarity_timer_")
)
colnames(df_all.long.familarity_timer)[colnames(df_all.long.familarity_timer) == "value"] <- "familarity_timer"
df_all.long.familarity_timer <- df_all.long.familarity_timer[, c("ID", "measurement", "familarity_timer")]

  
# trial number
df_all.long.trial_number <- df_all.long %>% filter(
  str_detect(measurement, "trial_number_")
)
colnames(df_all.long.trial_number)[colnames(df_all.long.trial_number) == "value"] <- "trial_number"
df_all.long.trial_number <- df_all.long.trial_number[, c("ID", "measurement", "trial_number")]



# checking to see columns match after merge
# grab last digit and compare
table(str_sub(df_all.long.accuracy_scale$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "accuracy_timer_")],-2))
table(str_sub(df_all.long.accuracy_timer$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "confidence_scale_")],-2))
table(str_sub(df_all.long.confidence_scale$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "confidence_timer_")],-2))
table(str_sub(df_all.long.confidence_timer$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "familarity_scale_")],-2))
table(str_sub(df_all.long.familarity_scale$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "familarity_timer_")],-2))
table(str_sub(df_all.long.familarity_timer$measurement,-2) == str_sub(df_all.long$measurement[str_detect(df_all.long$measurement, "trial_number_")],-2))


# now to combine the dfs, but with only 
df_all.tidy <- data.frame(df_all.long.accuracy_scale, 
                          df_all.long.accuracy_timer[,"accuracy_timer"],
                          df_all.long.confidence_scale[,"confidence_scale"],
                          df_all.long.confidence_timer[,"confidence_timer"],
                          df_all.long.familarity_scale[,"familarity_scale"],
                          df_all.long.familarity_timer[,"familarity_timer"],
                          df_all.long.trial_number[,"trial_number"]
                          )

# changing colnames
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.accuracy_timer....accuracy_timer.."] <- "accuracy_timer"
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.confidence_scale....confidence_scale.."] <- "confidence_scale"
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.confidence_timer....confidence_timer.."] <- "confidence_timer"
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.familarity_scale....familarity_scale.."] <- "familarity_scale"
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.familarity_timer....familarity_timer.."] <- "familarity_timer"
colnames(df_all.tidy)[colnames(df_all.tidy) == "df_all.long.trial_number....trial_number.."] <- "trial_number"



# changing measurement column to item number as it includes relevant info
colnames(df_all.tidy)[colnames(df_all.tidy) == "measurement"] <-"item_number"
df_all.tidy$item_number <- str_replace(df_all.tidy$item_number, "accuracy_scale_", "")
```


when coding the experiment, a way to identify which items belong to which batch (there are two) was not included. so this is a little hack to get this info.

```{r adding batch number as not included in experiment code,  include=FALSE}


# # adding batch details 
batch_1_items <- c("169", "141", "133", "127", "25", "39", "208", "218", "47", "147", "82", "204", "158", "151", "2", "157", "32", "191", "93", "200", "221", "137", "190", "205", "11", "12", "154", "210", "69", "98", "146", "125")

batch_2_items <- c("86", "174", "71", "160", "186", "76", "102", "55", "57", "116", "120", "173", "94", "22", "124", "14", "182", "171", "3", "83", "214", "209", "26", "48", "189", "44", "118", "166", "103", "161", "10", "130")


# whenever the item number matches that of an item number from the batch we add a "Batch X" qualifier 
df_all.tidy <- df_all.tidy %>% mutate(batch = case_when(
  item_number == batch_1_items[1] ~ "Batch 1",
  item_number == batch_1_items[2] ~ "Batch 1",
  item_number == batch_1_items[3] ~ "Batch 1",
  item_number == batch_1_items[4] ~ "Batch 1",
  item_number == batch_1_items[5] ~ "Batch 1",
  item_number == batch_1_items[6] ~ "Batch 1",
  item_number == batch_1_items[7] ~ "Batch 1",
  item_number == batch_1_items[8] ~ "Batch 1",
  item_number == batch_1_items[9] ~ "Batch 1",
  item_number == batch_1_items[10] ~ "Batch 1",
  item_number == batch_1_items[11] ~ "Batch 1",
  item_number == batch_1_items[12] ~ "Batch 1",
  item_number == batch_1_items[13] ~ "Batch 1",
  item_number == batch_1_items[14] ~ "Batch 1",
  item_number == batch_1_items[15] ~ "Batch 1",
  item_number == batch_1_items[16] ~ "Batch 1",
  item_number == batch_1_items[17] ~ "Batch 1",
  item_number == batch_1_items[18] ~ "Batch 1",
  item_number == batch_1_items[19] ~ "Batch 1",
  item_number == batch_1_items[20] ~ "Batch 1",
  item_number == batch_1_items[21] ~ "Batch 1",
  item_number == batch_1_items[22] ~ "Batch 1",
  item_number == batch_1_items[23] ~ "Batch 1",
  item_number == batch_1_items[24] ~ "Batch 1",
  item_number == batch_1_items[25] ~ "Batch 1",
  item_number == batch_1_items[26] ~ "Batch 1",
  item_number == batch_1_items[27] ~ "Batch 1",
  item_number == batch_1_items[28] ~ "Batch 1",
  item_number == batch_1_items[29] ~ "Batch 1",
  item_number == batch_1_items[30] ~ "Batch 1",
  item_number == batch_1_items[31] ~ "Batch 1",
  item_number == batch_1_items[32] ~ "Batch 1",
  item_number == batch_2_items[1] ~ "Batch 2",
  item_number == batch_2_items[2] ~ "Batch 2",
  item_number == batch_2_items[3] ~ "Batch 2",
  item_number == batch_2_items[4] ~ "Batch 2",
  item_number == batch_2_items[5] ~ "Batch 2",
  item_number == batch_2_items[6] ~ "Batch 2",
  item_number == batch_2_items[7] ~ "Batch 2",
  item_number == batch_2_items[8] ~ "Batch 2",
  item_number == batch_2_items[9] ~ "Batch 2",
  item_number == batch_2_items[10] ~ "Batch 2",
  item_number == batch_2_items[11] ~ "Batch 2",
  item_number == batch_2_items[12] ~ "Batch 2",
  item_number == batch_2_items[13] ~ "Batch 2",
  item_number == batch_2_items[14] ~ "Batch 2",
  item_number == batch_2_items[15] ~ "Batch 2",
  item_number == batch_2_items[16] ~ "Batch 2",
  item_number == batch_2_items[17] ~ "Batch 2",
  item_number == batch_2_items[18] ~ "Batch 2",
  item_number == batch_2_items[19] ~ "Batch 2",
  item_number == batch_2_items[20] ~ "Batch 2",
  item_number == batch_2_items[21] ~ "Batch 2",
  item_number == batch_2_items[22] ~ "Batch 2",
  item_number == batch_2_items[23] ~ "Batch 2",
  item_number == batch_2_items[24] ~ "Batch 2",
  item_number == batch_2_items[25] ~ "Batch 2",
  item_number == batch_2_items[26] ~ "Batch 2",
  item_number == batch_2_items[27] ~ "Batch 2",
  item_number == batch_2_items[28] ~ "Batch 2",
  item_number == batch_2_items[29] ~ "Batch 2",
  item_number == batch_2_items[30] ~ "Batch 2",
  item_number == batch_2_items[31] ~ "Batch 2",
  item_number == batch_2_items[32] ~ "Batch 2",
))

# checking count (why is this the same?)
table(df_all.tidy$batch)
```


it's time for some cleaning. keeping: 
- only first attempt (no multiple entries)
- those who have values for political identity for all participants
- at least three CRT responses

```{r multiple attemps removal,include=FALSE}

# df with just data of one trial (equivalent to having a wide format dataset)
one_trial <- df_all.tidy %>% dplyr::filter(trial_number == "6") #i choose trial number 6 because that is a trial where i don't have any missing data for any participant

# list of participants who tried more than once, seen through prolific ID
attempted_twice  <- data.frame(table(one_trial$PROLIFIC_PID))
attempted_twice <- attempted_twice[attempted_twice$Freq > 1,]
attempted_twice <- as.character(attempted_twice[["Var1"]])
attempted_twice

# listed now with subject id
attempted_twice <- one_trial %>% filter(PROLIFIC_PID %in% attempted_twice) %>% select(Subject, PROLIFIC_PID)

# sorting by subject number first, then prolific id
attempted_twice <- attempted_twice[order(attempted_twice$Subject),]
attempted_twice <- attempted_twice[order(attempted_twice$PROLIFIC_PID),]

# keeping only first attempt
attempted_twice <- attempted_twice[["Subject"]]
attempted_twice <- attempted_twice[seq(1,18,2)]
attempted_twice

# removing those 9 participants from dataframe
one_trial <- one_trial %>% dplyr::filter(!Subject %in% attempted_twice)
df_all.tidy <- df_all.tidy %>% dplyr::filter(!Subject %in% attempted_twice)

```



```{r political identity missing removal,include=FALSE}

#look through wide format to check for missing data
political_identity_wide <- one_trial %>% select(Subject, political_identification_scale, CRT_1, CRT_2, CRT_3, CRT_4)


# finding subject number of those with missing political identification
political_identity_missing <- political_identity_wide$Subject[is.na(political_identity_wide$political_identification_scale)]

# 5 in total, we will remove later
political_identity_missing


# removing those 5 participants from dataframe
one_trial <- one_trial %>% dplyr::filter(!Subject %in% political_identity_missing)
df_all.tidy <- df_all.tidy %>% dplyr::filter(!Subject %in% political_identity_missing)

```


```{r CRT missing removal, include=FALSE}
# now with regards to CRT
# need to count whether a participant has more than one missing value with CRT

# converting  to long again for better counting of CRT
CRT_long <- one_trial %>% select(Subject, ID, CRT_1, CRT_2, CRT_3, CRT_4)
CRT_long <- pivot_longer(CRT_long, !c(ID, Subject), names_to = "measurement", values_to = "value")

# finding those subjects with missing values
CRT_missing <- CRT_long %>% filter(is.na(value))
CRT_missing <- data.frame(table(CRT_missing$Subject))
CRT_missing <- CRT_missing %>% filter(!Freq == 1)
CRT_missing <- CRT_missing[["Var1"]]
CRT_missing <- as.numeric(as.character(CRT_missing))

# 26 in total with more than 1 CRT response missing
CRT_missing

# removing them from main df
# removing those 5 participants from dataframe
one_trial <- one_trial %>% dplyr::filter(!Subject %in% CRT_missing)
df_all.tidy <- df_all.tidy %>% dplyr::filter(!Subject %in% CRT_missing)

```


now to remove those participants who failed attention checks.
```{r attention check,  include=FALSE}

# df for attention checks
df_all.tidy.attention <- df_all.tidy %>% filter(item_number == "attention_check1" | item_number == "attention_check2")

# checking to see if there are NA values
attention_check_remove_1 <- df_all.tidy.attention %>% filter(is.na(accuracy_scale) |
                                   is.na(confidence_scale) |
                                   is.na(familarity_scale)
                                   )

# 2 people with missing data with attention check questions will be removed 
attention_check_remove_1 <- attention_check_remove_1[["Subject"]]

# removing participant with NA values for remainder of checking
df_all.tidy.attention <- df_all.tidy.attention %>%
  drop_na(accuracy_scale) %>%
  drop_na(confidence_scale) %>%
  drop_na(familarity_scale)

# new summary columns
df_all.tidy.attention$attention_check_accuracy <- NA
df_all.tidy.attention$attention_check_confidence <- NA
df_all.tidy.attention$attention_check_familarity <- NA

for (i in 1:length(df_all.tidy.attention$item_number)) {

  # accuracy scale
  if (df_all.tidy.attention$item_number[i] == "attention_check1" && df_all.tidy.attention$accuracy_scale[i] == "Yes") {
    df_all.tidy.attention$attention_check_accuracy[i] <- "Correct"
  } else if (df_all.tidy.attention$item_number[i] == "attention_check2" && df_all.tidy.attention$accuracy_scale[i] == "No") {
    df_all.tidy.attention$attention_check_accuracy[i] <- "Correct"
  } else {
    df_all.tidy.attention$attention_check_accuracy[i] <- "Incorrect"
  }

  # partisan scale
  if (df_all.tidy.attention$item_number[i] == "attention_check1" && df_all.tidy.attention$confidence_scale[i] == 3) {
    df_all.tidy.attention$attention_check_confidence[i] <- "Correct"
  } else if (df_all.tidy.attention$item_number[i] == "attention_check2" && df_all.tidy.attention$confidence_scale[i] == 5) {
    df_all.tidy.attention$attention_check_confidence[i] <- "Correct"
  } else {
    df_all.tidy.attention$attention_check_confidence[i] <- "Incorrect"
  }

  # familarity scale
  if (df_all.tidy.attention$item_number[i] == "attention_check1" && df_all.tidy.attention$familarity_scale[i] == "Yes") {
    df_all.tidy.attention$attention_check_familarity[i] <- "Correct"
  } else if (df_all.tidy.attention$item_number[i] == "attention_check2" && df_all.tidy.attention$familarity_scale[i] == "No") {
    df_all.tidy.attention$attention_check_familarity[i] <- "Correct"
  } else {
    df_all.tidy.attention$attention_check_familarity[i] <- "Incorrect"
  }
}

df_all.tidy.attention$accuracy_scale <- as.factor(df_all.tidy.attention$accuracy_scale)
df_all.tidy.attention$confidence_scale <- as.factor(df_all.tidy.attention$confidence_scale)
df_all.tidy.attention$familarity_scale <- as.factor(df_all.tidy.attention$familarity_scale)
df_all.tidy.attention$item_number <- as.factor(df_all.tidy.attention$item_number)


# list of those who got attention check wrong
attention_check_remove_2 <- df_all.tidy.attention %>%
  dplyr::select(Subject, item_number, attention_check_accuracy, attention_check_confidence, attention_check_familarity) %>%
  group_by(Subject) %>%
  dplyr::filter(attention_check_accuracy == "Incorrect" | attention_check_confidence == "Incorrect" | attention_check_familarity == "Incorrect") %>%
  count() %>%
  dplyr::filter(n > 1)

attention_check_remove_2 <- attention_check_remove_2[["Subject"]]

# final list
attention_check_remove <- c(attention_check_remove_1, attention_check_remove_2)

# removing those 30 participants from dataframe
one_trial <- one_trial %>% dplyr::filter(!Subject %in% attention_check_remove)
df_all.tidy <- df_all.tidy %>% dplyr::filter(!Subject %in% attention_check_remove)
```

```{r removing attention check data from main df}

# df without attention checks
df_all.tidy <- df_all.tidy %>% filter(item_number != "attention_check1", item_number != "attention_check2")

```


these 4 have lots of missing data (152214, 152389, 152441, 152572) - not sure what to do with them? #COMMENT
always responding with the same response

```{r checking for always true or false for accuracy question}

# checking for participants who always said accurate versus inaccurate
#  if average is either 0 or 1, they they chose no or yes throughout
check_all_true_or_false <- df_all.tidy %>%
  drop_na(accuracy_scale) %>%
  dplyr::select(Subject, item_number, accuracy_scale) %>%
  group_by(Subject, item_number) %>%
  dplyr::filter(!accuracy_scale %in% "undefined") %>%
  mutate(accuracy_scale1 = case_when(accuracy_scale == "Yes" ~ 1,
                                      accuracy_scale == "No" ~ 0)) %>%
  group_by(Subject) %>%
  summarise(mean_yes_no = mean(accuracy_scale1), count = n(), SD = sd(accuracy_scale1), se = (SD / (sqrt(count))))

# checking to see how many don't have 32 responses 
index_full_32 <- check_all_true_or_false %>% dplyr::filter(count != 32)
index_full_32 <- index_full_32[["Subject"]]

check_all_true_or_false <- check_all_true_or_false %>%
  dplyr::filter(mean_yes_no == 0 | mean_yes_no == 1) %>%
  dplyr::filter(SD == 0 | se == 0)

# 4 participants who always responded either true of false
check_all_true_or_false_remove <- check_all_true_or_false[["Subject"]]


# checking for participants who always used one confidence scale response
#  if average is either  1,2,3,4,5,6 and SD = 0, they they chose one option throughout
check_all_confidence_ratings <- df_all.tidy %>%
  dplyr::select(Subject, item_number, confidence_scale) %>%
  drop_na(confidence_scale) %>%
  group_by(Subject, item_number) %>%
  dplyr::filter(!confidence_scale %in% "undefined")

check_all_confidence_ratings <- check_all_confidence_ratings %>%
  group_by(Subject) %>%
  summarise(mean_confidence = mean(as.numeric(as.character(confidence_scale))), count = n(), SD = sd(as.numeric(as.character(confidence_scale))), se = (SD / (sqrt(count))))

check_all_confidence_ratings <- check_all_confidence_ratings %>%
  dplyr::filter(mean_confidence == 1 | mean_confidence == 2 | mean_confidence == 3 | mean_confidence == 4 | mean_confidence == 5 | mean_confidence == 6) %>%
  dplyr::filter(SD == 0)

# 3 participants who gave only one confidence score response
check_all_confidence_ratings_remove <- check_all_confidence_ratings[["Subject"]]

# combining both indexes
low_effort_response_remove <- c(check_all_true_or_false_remove, check_all_confidence_ratings_remove)


# removing those 7 participants from dataframe
one_trial <- one_trial %>% dplyr::filter(!Subject %in% low_effort_response_remove)
df_all.tidy <- df_all.tidy %>% dplyr::filter(!Subject %in% low_effort_response_remove)

```

as a final step we are going to add CRT data to the long df

```{r creating a CRT dataset}

CRT <- one_trial %>%
  dplyr::select(Subject, CRT_1, CRT_2, CRT_3, CRT_4, CRT_5, condition)


# creating a function to input right answer
# CRT_1
CRT_1_function <- function(response) {
  verdict <- str_detect(response, "second|Second|SECOND|2")

  return(verdict)
}

# CRT_2
CRT_2_function <- function(response) {
  verdict <- str_detect(response, "eight|Eight|EIGHT|8")

  return(verdict)
}

# CRT_3
CRT_3_function <- function(response) {
  verdict <- str_detect(response, "zero|Zero|hole|Hole|HOLE|emply|Empty|EMPTY|no|No|NO|0")

  return(verdict)
}

# CRT_4
CRT_4_function <- function(response) {
  verdict <- str_detect(response, "emily|Emily|EMILY")

  return(verdict)
}

# scoring responses
CRT <- CRT %>% mutate(CRT_1_Clean = ifelse(CRT_1_function(CRT_1) == TRUE, 1, 0),
                      CRT_2_Clean = ifelse(CRT_2_function(CRT_2) == TRUE, 1, 0),
                      CRT_3_Clean = ifelse(CRT_3_function(CRT_3) == TRUE, 1, 0),
                      CRT_4_Clean = ifelse(CRT_4_function(CRT_4) == TRUE, 1, 0))

CRT$CRT_5_Clean <- as.factor(CRT$CRT_5)

# also for the larger dataset
df_all.tidy <- df_all.tidy %>% mutate(CRT_1_Clean = ifelse(CRT_1_function(CRT_1) == TRUE, 1, 0),
                      CRT_2_Clean = ifelse(CRT_2_function(CRT_2) == TRUE, 1, 0),
                      CRT_3_Clean = ifelse(CRT_3_function(CRT_3) == TRUE, 1, 0),
                      CRT_4_Clean = ifelse(CRT_4_function(CRT_4) == TRUE, 1, 0))

df_all.tidy$CRT_5_Clean <- as.factor(df_all.tidy$CRT_5)

CRT_Clean <- CRT %>% dplyr::select(Subject, CRT_1_Clean, CRT_2_Clean, CRT_3_Clean, CRT_4_Clean, CRT_5_Clean, condition)

# counting number of questions correct and number of questions incorrect
CRT_Clean <- CRT_Clean %>% 
  # mutate_at(vars(CRT_1_Clean,CRT_2_Clean,CRT_3_Clean,CRT_4_Clean), ~replace_na(., 0)) %>%
  mutate(
  total_correct = CRT_1_Clean + CRT_2_Clean + CRT_3_Clean + CRT_4_Clean
  ) 


# taking care of participants with missing numbers. here we get total score out of the questions they answered in total.
CRT_Clean$total_correct[CRT_Clean$Subject == "152431"] <- 1
CRT_Clean$total_correct[CRT_Clean$Subject == "154599"] <- 2


# adding column for total answered to create percentages
CRT_Clean <- CRT_Clean %>% dplyr::mutate(total_answered = 4)

# manually changing total answered for those with less than 4 answered
CRT_Clean$total_answered[CRT_Clean$Subject == "152431"] <- 3
CRT_Clean$total_answered[CRT_Clean$Subject == "154599"] <- 3


CRT_Clean <- CRT_Clean %>%
  mutate(
    CRT_proficiency = case_when(
      total_correct >= 3 ~ 1,
      total_correct <= 2 ~ 0,
    )
  ) %>%
  select(Subject, condition, CRT_1_Clean, CRT_2_Clean, CRT_3_Clean, CRT_4_Clean, CRT_5_Clean, CRT_proficiency,total_correct, total_answered) %>% 
  rename(CRT_1 = CRT_1_Clean, CRT_2 = CRT_2_Clean, CRT_3 = CRT_3_Clean, CRT_4 = CRT_4_Clean, CRT_5 = CRT_5_Clean) %>%
  mutate(CRT_proficiency_binary = case_when(CRT_proficiency == 1 ~ "High",
                                           CRT_proficiency == 0 ~ "Low"))

# creating percentages
CRT_Clean <- CRT_Clean %>% dplyr::mutate(percent_correct = (total_correct/total_answered))

standard_CRT_Clean <- CRT_Clean %>%
  summarise(mean = mean(percent_correct), SD = sd(percent_correct), two_SD = SD*2, count = n(), se = (SD / (sqrt(count))), median = median(percent_correct), min = min(percent_correct), max = max(percent_correct))

# adding standardised values
CRT_Clean <- CRT_Clean %>% dplyr::mutate(percent_correct_standard = (percent_correct - standard_CRT_Clean$mean[1])/standard_CRT_Clean$two_SD[1])


CRT_subject_index <- CRT_Clean[["Subject"]]


# string detect all of the values that are item number x and then add that to true_false of my df
for (i in 1:length(CRT_subject_index)) {
  # crt percentage 
  df_all.tidy$CRT_percent[df_all.tidy$Subject == CRT_subject_index[i]] <- CRT_Clean$percent_correct[i]
  # crt percentage standard
  df_all.tidy$CRT_standard[df_all.tidy$Subject == CRT_subject_index[i]] <- CRT_Clean$percent_correct_standard[i]
  # crt binary
  df_all.tidy$CRT_binary[df_all.tidy$Subject == CRT_subject_index[i]] <- CRT_Clean$CRT_proficiency_binary[i]
}

# creating a long df
CRT_Clean.long <- CRT_Clean %>%
  dplyr::select(Subject, condition, CRT_1, CRT_2, CRT_3, CRT_4, CRT_5, percent_correct, percent_correct_standard,CRT_proficiency_binary) %>%
  gather(CRT, response, -c(Subject, condition, percent_correct, percent_correct_standard, CRT_5, CRT_proficiency_binary))

```



ready to save for analyses.
```{r final save,  include=FALSE}

# before save, re-doing subject ID so it's in sequence.
# adding ID number column relative to subject number
unique_subjects <- unique(df_all.tidy$Subject)
number_subjects <- seq(1,length(unique_subjects), 1)

for (i in 1:length(unique_subjects)) {
  
  df_all.tidy$ID[df_all.tidy$Subject == unique_subjects[i]] <- number_subjects[i]

}


# renaming some columns for final dataset
#please note familiarity has been throughout so that's why we rename here twice
df_all.tidy <- df_all.tidy %>%
  rename(accuracy_response = accuracy_scale,
              confidence_response = confidence_scale,
              familiarity_response = familarity_scale,
              familiarity_timer = familarity_timer)


# whole dataset
write_xlsx(
  df_all.tidy,
  path = here("Data", "Clean", "cleaned_data.xlsx"),
  col_names = TRUE)


```

